---
title: "Text Mining"
output: html_document
date: '2022-12-03'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part A:

In this section, we will be performing the bag of words analysis. After relevant analysis, the results will enable us to find the important words by ratings. The word analysis will be done in different n-gram levels (unigram, bigram and trigram). 

Upon finding out the important words, we will visualize them in bar plots and wordclouds.

Finally, we will also perform some analysis to connect word importance with different components of the available metadata.

For this dataset, we will perform each step on the review level as well as on the company level.

* Loading the relevant libraries
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center")
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidytext)
library(jsonlite)
library(tidyr)
library(readr)
library(topicmodels)
library(geojsonR)
library(stringr)
library(dplyr)
library(tidyr)
library(stm)
library(udpipe)
library(cld2)
library(wordcloud)
library(xml2)
library(rvest)
library(janeaustenr)
library(data.table)
library(rjson)
library(lubridate)
library(textcat)
library(rJava)
library(qdap)
library(magrittr)
library(jsonlite)
library(topicmodels)
library(geojsonR)
library(hunspell)
library(ggrepel)
library(gridExtra)
library(widyr)
library(igraph)
library(textstem)
library(ggraph)
library(stringr)
library(future)
library(future.apply)
library(influential)
library(stringi)
library(tm)
```

# Data Preparation

## Ingest

We will now perform scraping with rvest to retrieve information from Trustpilot webpage.

```{r eval=FALSE}
#Creating a dataset to store all the scraped data
rm(store_reviews)
store_reviews <- data.frame()

#Defining functions to repeatedly perform specific crawling
get_description = function(store_links) {
  store_page = read_html(store_links)
  description = store_page %>% html_nodes("div.card_cardContent__sFUOe") %>% html_node("div.styles_container__9nZxD") %>% html_text() %>% .[c(1,2,3)] %>% paste0(collapse = " ")
  return(description)
}

get_email = function(store_links) {
  store_page = read_html(store_links)
  email = store_page %>% html_nodes("div.card_cardContent__sFUOe") %>% html_node(".styles_contactInfoElement__SxlS3:nth-child(1) .styles_contactInfoLink__gMJWX") %>% html_text() %>% .[c(1,2,3)] %>% paste0(collapse = " ") 
  return(email)
}

get_phone = function(store_links) {
  store_page = read_html(store_links)
  phone = store_page %>% html_nodes("div.card_cardContent__sFUOe") %>% html_node(".styles_contactInfoElement__SxlS3+ .styles_contactInfoElement__SxlS3 .styles_contactInfoLink__gMJWX") %>% html_text() %>% .[c(1,2,3)] %>% paste0(collapse = " ")
  return(phone)
}

get_address = function(store_links) {
  store_page = read_html(store_links)
  address = store_page %>% html_nodes("div.card_cardContent__sFUOe") %>% html_node("ul.typography_typography__QgicV") %>% html_text() %>% .[c(1,2,3)] %>% paste0(collapse = " ")
  return(address)
}

#Looping through multiple pages and subpages and retrieving data into the desired dataset
for (page_result in seq(from = 1, to = 750, by = 15)) {
  rm(sub_contents)
  sub_contents <- data.frame()
  
  link = paste0("https://www.trustpilot.com/categories/travel_agency?page=", page_result)
  page = read_html(link)
  
  name = page %>% html_nodes("div.styles_content__3mwYr") %>% html_node(".styles_displayName__1LIcI") %>% html_text()
                                                                                        
  overall = page %>% html_nodes("div.styles_rating__2FRLX") %>% html_nodes("span.styles_mobile__17MXv") %>% html_text()
  
  category = page %>% html_nodes("div.card_cardContent__3Idve") %>% html_node("div.styles_wrapper__nFO8_") %>% html_text() %>% sub("·.*", "", .)
                                                                                        Sys.sleep(1)
  total_reviews = page %>% html_nodes("div.styles_rating__2FRLX") %>% html_node("p.typography_typography__23IQz") %>% html_text() 
                                                                                                                                                    
  store_links <- page %>% 
                 html_nodes("div.paper_paper__29o4A") %>%
                 html_node(".styles_linkWrapper__3x9X7") %>% 
                 html_attr("href") %>% 
                 paste0("https://uk.trustpilot.com",.)
  
  store_description = sapply(store_links, FUN = get_description, USE.NAMES = F)
  Sys.sleep(2)
  phone_number = sapply(store_links, FUN = get_phone, USE.NAMES = F)
  
  email = sapply(store_links, FUN = get_email, USE.NAMES = F)
  Sys.sleep(2)
  store_address = sapply(store_links, FUN = get_address, USE.NAMES = F)
                
  for (i in store_links) {
    rm(sub_contents_catch)
    sub_contents_catch <- data.frame()
    
    for (subpage_result in seq(from = 1, to = 3, by = 1)) {
      sub_links = paste0(i, "?page=", subpage_result)
      sub_page = read_html(sub_links)
      
      reviewer = sub_page %>% html_nodes("div.styles_consumerDetailsWrapper__p2wdr") %>%
              html_node("div.typography_typography__QgicV") %>%
             html_text(trim = TRUE) %>% paste0(collapse = "//")
                                                                                        Sys.sleep(1)
      review_summary = sub_page %>% html_nodes("div.styles_reviewContent__0Q2Tg") %>%
              html_node("a.link_internal__7XN06") %>%
             html_text(trim = TRUE) %>% paste0(collapse = "//")
                                                                                        Sys.sleep(2)
      
      review = sub_page %>% html_nodes("div.styles_reviewContent__0Q2Tg") %>% html_node("p.typography_typography__QgicV") %>% html_text() %>%   
        paste0(collapse = "//")
                                                                                        Sys.sleep(2)
      date = sub_page %>% html_nodes("div.styles_reviewHeader__iU9Px") %>%
            html_node("div.typography_typography__QgicV time") %>%
             html_attr("datetime") %>% str_sub(.,1, 10) %>% paste0(collapse = "//")
                                                                                        
      country = sub_page %>% html_elements(xpath = "//div[contains(@class, 'styles_consumerDetailsWrapper__p2wdr')]") %>%
            html_elements(xpath = ".//div[contains(@class, 'styles_consumerExtraDetails__fxS4S')]") %>%
            html_node(".styles_detailsIcon__Fo_ua+ .styles_detailsIcon__Fo_ua") %>%
            html_text(trim = TRUE) %>% paste0(collapse = "//")
                                                                                        Sys.sleep(2)
      reviewer_rating = sub_page %>% html_nodes("div.styles_reviewHeader__iU9Px") %>%
            html_node("div.star-rating_starRating__4rrcf img") %>% html_attr("alt") %>%  paste0(collapse = "//")
      
      sub_contents_catch = rbind(sub_contents_catch, data.frame(reviewer, review_summary, review, date, country, reviewer_rating))
    
      ifelse(subpage_result == 5, t(sub_contents_catch) %>% as.data.frame() %>% unite(col = "1", sep = "//") %>% t(.) -> sub_contents_catch, print(paste("Sub_Page", subpage_result)))
      
    }
    sub_contents = rbind(sub_contents, sub_contents_catch)
  }
                                                                                        
  store_reviews <- rbind(store_reviews, 
                         data.frame(name, overall, category, store_description, phone_number, email, store_address, sub_contents, stringsAsFactors = FALSE))
                                                                                       
  print(paste("Page:", page_result))
}
#saveRDS(store_reviews, "store_reviews_final.rds)
```

* Transforming the scraped data

Now that the raw data is taken, we will perform some steps to convert it into analysable form.

```{r eval=FALSE}
#Reading the saved file
dataset <- readRDS("store_reviews_finals.rds")
dataset <- distinct(dataset)

#Correcting an anomaly
dataset$review[400] <- str_replace(dataset$review[400], "https://earnapp", "https:earnapp")
dataset$review[68] <- str_replace(dataset$review[68], " // ", "")
dataset$review[609] <- str_replace(dataset$review[609], " //M", "M")
dataset$review[862] <- str_replace(dataset$review[862], "on 2//7/09-as", "on 2/7/09-as")
dataset$review[902] <- str_replace(dataset$review[902], "https:// t.me", "https: t.me")
dataset$review[930] <- str_replace(dataset$review[930], "\\\\WHY///", "WHY")

#Separating the individual reviews
dataset <- dataset %>% separate_rows(7:12, sep = "//")

#Removing duplicates
dataset <- distinct(dataset)
dataset <- na.omit(dataset)
dataset <- dataset %>% filter(reviewer_rating != "")

#Saving the final dataset
#saveRDS(dataset, "raw_data_final.rds")
```

* Cleaning the variables

For the benefit of analysis, we will perform some cleaning to normalize the dataset. We utilized some techniques while scraping to ensure the row numbers match. We will now remove those unnecessary characters.

```{r}
review_data <- readRDS("raw_data_final.rds")
#Removing unwanted characters
review_data$store_description <- review_data$store_description %>% str_replace_all("NA", "")
review_data$email <- review_data$email %>% str_replace_all("NA", "")
review_data$store_address <- review_data$store_address %>% str_replace_all("NA", "")
review_data$phone_number <- review_data$phone_number %>% str_replace_all("NA", "")
review_data$reviewer_rating <- review_data$reviewer_rating %>% str_sub(start = 6, end = 8)

#Fixing the datatypes
review_data <- review_data %>% separate(date, into = c("year", "month", "day"), sep = "-")
review_data <- review_data %>% mutate(year = as.numeric(year),
                                           month = as.numeric(month),
                                           day = as.numeric(day))
review_data <- review_data %>% mutate(date = make_date(year, month, day))
review_data$date <- as.Date(review_data$date, format = "%Y %b,%d")

#Formatting the target variable
review_data$overall <- as.numeric(review_data$overall)
review_data$overall <- round(review_data$overall)
review_data$reviewer_rating <- as.numeric(review_data$reviewer_rating)

review_data <- review_data %>% arrange(desc(date))
```

The dataset is now ready for text analysis

## Prepare

We will now perform some modificatios on the reviews to bring it into a better format to analyse

```{r}
#Remove companies with less than 5 reviews
remove_names <- review_data %>% 
                group_by(name) %>% 
                summarise(total = n()) %>% 
                filter(total <= 5) %>% pull(name)

review_data <- review_data %>% 
               filter(!(name %in% remove_names))

#Assign unique keys to the stores
name_id <- review_data %>% distinct(name)
name_id$company_id <- 1:nrow(name_id)
review_data <- name_id %>%  
               inner_join(review_data)
              
#Create a new key to track each review
review_data$review_id <- 1:nrow(review_data)

#Create new object with only the full review text and the review_id
reviews<- review_data %>% 
          dplyr::select(review_id, review_summary, review, reviewer_rating) 

reviews <- reviews %>% 
           mutate(reviewText = 
           paste(
             coalesce(review_data$review_summary, ""),
             coalesce(review_data$review, "")
             )
         )  %>%
  dplyr::select(-(review_summary:review)) 

review_data <- review_data %>% left_join(reviews)
```

* Cleaning the reviews

We will perform some basic text cleaning functions, which can be utilized throughout all the parts of this project.

```{r}
#Replacing the digits with empty space
review_data$reviewText <- gsub('[[:digit:]]+',' ', review_data$reviewText)

#Replacing the punctuations with empty space
review_data$reviewText <- gsub('[[:punct:]]+',' ', review_data$reviewText)

#Additional cleaning
review_data$reviewText <- bracketX(review_data$reviewText)
review_data$reviewText <- replace_contraction(review_data$reviewText)
review_data$reviewText <- replace_symbol(review_data$reviewText)

# Remove spaces and newlines
review_data$reviewText <- gsub("\n", " ", review_data$reviewText)
review_data$reviewText <- gsub("^\\s+", "", review_data$reviewText)
review_data$reviewText <- gsub("\\s+$", "", review_data$reviewText)
review_data$reviewText <- gsub("[ |\t]+", " ", review_data$reviewText) #spaces


#Getting the character lengths
review_data$char_length <- nchar(review_data$reviewText)

#Plotting the lengths 
hist(review_data$char_length, breaks = 300, main = "Review Lengths")

#Filtering for minimum length of 100
review_data <- review_data %>% filter(char_length>100)
hist(review_data$char_length,breaks = 300,main = "Review Length -Left trim to 100")

#Filtering for maximum length of 1400
review_data <- review_data %>% filter(char_length<1400)
hist(review_data$char_length,breaks = 300,main = "Review Length(All) -Right trim to 1000")

#Cleaning the language of the reviews
review_data$reviewText <- iconv(review_data$reviewText)
review_data$language <- cld2::detect_language(review_data$reviewText)
review_data %>% filter(language =="en") -> review_data_en
```

* Cleaning the store descriptions
```{r}
#Replacing the digits with empty space
review_data_en$store_description <- gsub('[[:digit:]]+',' ', review_data_en$store_description)

#Replacing the punctuations with empty space
review_data_en$store_description <- gsub('[[:punct:]]+',' ', review_data_en$store_description)

#Additional cleaning
review_data_en$store_description <- bracketX(review_data_en$store_description)
review_data_en$store_description <- replace_contraction(review_data_en$store_description)
review_data_en$store_description <- replace_symbol(review_data_en$store_description)

# Remove spaces and newlines
review_data_en$store_description <- gsub("\n", " ", review_data_en$store_description)
review_data_en$store_description <- gsub("^\\s+", "", review_data_en$store_description)
review_data_en$store_description <- gsub("\\s+$", "", review_data_en$store_description)
review_data_en$store_description <- gsub("[ |\t]+", " ", review_data_en$store_description) #spaces

#Lemmatizing
lemma <- review_data_en %>% dplyr::select(company_id, store_description) %>% distinct(.)
lemma <- lemma %>% unnest_tokens(word, store_description)
lemma$word <- lemmatize_words(lemma$word)
lemma <- lemma %>% group_by(company_id) %>% summarise(store_description = paste(word, collapse = " "))
review_data_en$store_description <- NULL
review_data_en <- review_data_en %>% left_join(lemma)

#Cleaning the language
review_data_en$store_description <- iconv(review_data_en$store_description)
```

* Checking mistakes in reviews

We will use the 'hunspell' dictionary spelling suggestion to deal will the spelling mistakes identified in the reviews. Then, using judgement, we will manually fix the mistakes

```{r}
#Getting the reviews column
reviews <- review_data_en %>% arrange(review_id) %>% dplyr::select(review_id,reviewText)

#Tokenizing the reviews
tokens_for_spellcheck <- unnest_tokens(reviews,word,reviewText)

#Getting the unique words
unique_words <- unique(tokens_for_spellcheck$word)
head(unique_words)
length(unique_words)

#Finding the misspelled words
mispells <- hunspell(unique_words)

#Getting the unique spelling mistake
mispells <- unique(unlist(mispells))
length(mispells)

#Getting correct word suggestions
suggestive_words <- hunspell_suggest(mispells)
suggestive_words <- unlist(lapply(suggestive_words, function(x) x[1]))
head(suggestive_words)
mistakes.list <- as.data.frame(cbind(mispells,suggestive_words))
freq_mistake <- count(tokens_for_spellcheck,word)
freq_mistake <- inner_join(freq_mistake, mistakes.list, by = c("word" = "mispells"))
words_suggestion<-arrange(freq_mistake,desc(n))
word_NA <- words_suggestion %>% filter(is.na(suggestive_words))

#Manually dealing with the spelling suggestions
#write.csv(words_suggestion,"words_suggestion.csv")
#write.csv(word_NA,"word_NA.csv")

#Reading the prepared data
words_suggestion <- read.csv("words_suggestion.csv")
words_suggestion <- words_suggestion %>% dplyr::select(-X) %>% na.omit()
word_NA <- read.csv("word_NA.csv")
word_NA <- word_NA %>% dplyr::select(-X) %>% na.omit()

words_suggestions <- rbind(words_suggestion,word_NA)
words_suggestions <- arrange(words_suggestions)
sum(is.na(words_suggestions))

#Saving the final data
#write.csv(words_suggestions, "words_suggestions.csv")

#Replacing the mistakes words with suggestive ones
word.list <- read.csv("words_suggestions.csv", stringsAsFactors = FALSE)
mistake.words <- paste0(" ", word.list$word, " ")
correct.words <- paste0(" ", word.list$suggestive_words, " ")

mistake.replace <- function(df) {
 df$reviewText <- stri_replace_all_regex(df$reviewText, mistake.words, correct.words, vectorize_all = FALSE)
 return(df)
}

#Defining the number of cores
ncores <- 6L
plan(multiprocess, workers = ncores)

# split comments based on available cores
corpus_splitted <- split(reviews, seq(1, nrow(reviews), by=5))
reviews <- future_lapply(corpus_splitted, mistake.replace)
reviews <- rbindlist(reviews)
reviews <- as.data.frame(reviews)
reviews <- reviews %>% arrange(review_id)

#Creating a backup of the correct reviews
#saveRDS(reviews, "spell_mistake_correction.rds")

#Replacing the reviews with the corrected reviews
review_data_en$reviewText <- reviews$reviewText

#Creating a backup
#saveRDS(review_data_en, "review_data_en.rds")
```

* Tokenizing the reviews for stores
```{r}
#Grouping the reviews by stores
review_data_by_stores <- review_data_en %>%
 unnest_tokens(word,reviewText)%>%
 group_by(company_id) %>%
 summarise(grouped_reviews = paste(word,collapse = " "))

#saveRDS(review_data_by_stores, "review_data_by_stores.rds")

#Splitting the dataset
split_size <- 100

tokens_list <- split(review_data_by_stores,
                      rep(1:ceiling(nrow(review_data_by_stores)/split_size),
                      each=split_size,
                      length.out=nrow(review_data_by_stores)))

# Tokenization
review_tokens_by_stores <- data.frame()

for(i in 1:length(tokens_list)){
      review_tokens_k <- tokens_list[[i]] %>%
      unnest_tokens(word,grouped_reviews) %>%
      count(word,company_id) %>%
      anti_join(stop_words)
      print(i)
 
      review_tokens_by_stores <- bind_rows(review_tokens_by_stores,review_tokens_k)
}

#Lemmatizing the tokens
review_tokens_by_stores$word <- lemmatize_words(review_tokens_by_stores$word)
```

* Filtering the tokens

We will try to even trim the reviews by looking at the word lengths.

```{r}
#Finding the token lengths
review_tokens_by_stores$token_length <- nchar(review_tokens_by_stores$word)

#Checking the distribution of the lengths
view(review_tokens_by_stores %>% group_by(token_length) %>% summarise(total =n()))

#Removing the short tokens
review_tokens_by_stores <- review_tokens_by_stores %>% filter(token_length > 2)

#Checking the longest tokens
view(review_tokens_by_stores %>% group_by(token_length) %>% summarise(total =n()) %>% arrange(desc(token_length)))

#Removing excessively long tokens
review_tokens_by_stores <- review_tokens_by_stores %>% filter(token_length<=16)

#Creating backups
#saveRDS(review_data_by_stores, "review_data_by_stores.rds")

#Getting the frequency of each token
review_tokens_by_stores <- review_tokens_by_stores %>% count(company_id, word, sort = TRUE)
get_overall <- review_data_en %>% dplyr::select(., c(2,3)) %>% distinct(company_id, overall)
review_tokens_by_stores <- review_tokens_by_stores %>% left_join(get_overall)
total_words <- review_tokens_by_stores %>% 
                group_by(word) %>% 
                 summarize(total = sum(n))
review_tokens_by_stores <- review_tokens_by_stores %>% left_join(total_words)

#Calculating tf_idf of the tokens
review_tf_idf_by_stores <- review_tokens_by_stores %>% count(company_id, word) %>%
                            bind_tf_idf(word,company_id,n) %>% group_by(word) %>% arrange(desc(tf-idf))

#Checking the tf-idf distribution
hist(review_tf_idf_by_stores$tf_idf,breaks = 200,main="TF-IDF plot")

#Taking the cut-off value from histogram
review_tf_idf_by_stores <- review_tf_idf_by_stores %>% 
                            filter(tf_idf < 0.1)
hist(review_tf_idf_by_stores$tf_idf,breaks = 400,main="TF-IDF plot")

review_tf_idf_by_stores <- review_tf_idf_by_stores %>% 
                            filter(tf_idf<0.05)
hist(review_tf_idf_by_stores$tf_idf,breaks = 400,main="TF-IDF plot")

review_tf_idf_by_stores <- review_tf_idf_by_stores %>% 
                            filter(tf_idf>0.002)
hist(review_tf_idf_by_stores$tf_idf,breaks = 400,main="TF-IDF plot")

review_tf_idf_by_stores %>% group_by(word) %>%
                            summarise(total =n()) %>%
                            arrange(desc(total)) %>%
                            top_n(50)
```

* Visualizing wordclouds by ratings

```{r}
custom_words <- c("class", "please", "job", "shop", "hand", "friend", "date", "service", "review", "product", "customer", "day", "days", "received", "money", "week", "buy", "company", "phone", "don", "ve", "ofcom", "ninja", "moonfruit", "cancelled", "virgin", "told", "people", "arrived", "paul", "av", "ben", "josh", "andy", "tom", "richer", "plugin", "amp", "hifi", "aquiss", "sounds", "controller", "zoltan", "ian", "idnet", "glue", "proxy", "helen", "eno", "oled", "sypwai", "george", "peter", "panamoz", "pine", "dotsquares", "laura", "vape", "amiga", "biz", "technoworld", "proxies", "star", "hesit", "futur", "easi", "instal", "satisfi", "effici", "solv", "refus", "disgrac", "competit", "ensur", "refus", "incr", "wix", "sb", "laskys", "responsiv", "wayv", "dab", "novads", "harvey")

tibble(word = custom_words,lexicon = rep("custom",length(custom_words))) %>% bind_rows(stop_words) -> custom_stopwords
```

```{r}
review_5 <- review_tokens_by_stores %>%
            anti_join(custom_stopwords) %>%
            filter(overall == 5) %>%
            group_by(word) %>%
            summarise(total = mean(total)) %>%
            arrange(desc(total))

wordcloud(review_5$word, review_5$total, max.words = 25,
          colors = c("gold3", "blue4", "darkgoldenrod4"))
```
Word Cloud for 5 star reviews

```{r}
review_4 <- review_tokens_by_stores %>%
            anti_join(custom_stopwords) %>%
            filter(overall == 4) %>%
            group_by(word) %>%
            anti_join(custom_stopwords) %>%
            summarise(total = mean(total)) %>%
            arrange(desc(total))

wordcloud(review_4$word, review_4$total, max.words = 25,
          colors = c("gold3", "blue4", "darkgoldenrod4"))
```
Word Cloud for 4 star reviews

```{r}
review_3 <- review_tokens_by_stores %>%
            anti_join(custom_stopwords) %>%
            filter(overall == 3) %>%
            group_by(word) %>%
            anti_join(custom_stopwords) %>%
            summarise(total = mean(total)) %>%
            arrange(desc(total))

wordcloud(review_3$word, review_3$total, max.words = 25,
          colors = c("gold3", "blue4", "darkgoldenrod4"))
```
Word Cloud for 3 star reviews

```{r}
review_2 <- review_tokens_by_stores %>%
            anti_join(custom_stopwords) %>%
            filter(overall == 2) %>%
            group_by(word) %>%
            anti_join(custom_stopwords) %>%
            summarise(total = mean(total)) %>%
            arrange(desc(total))

wordcloud(review_2$word, review_2$total, max.words = 25,
          colors = c("gold3", "blue4", "darkgoldenrod4"))
```
Word Cloud for 2 star reviews

```{r}
review_1 <- review_tokens_by_stores %>%
            anti_join(custom_stopwords) %>%
            filter(overall == 1) %>%
            group_by(word) %>%
            anti_join(custom_stopwords) %>%
            summarise(total = mean(total)) %>%
            arrange(desc(total))

wordcloud(review_1$word, review_1$total, max.words = 25,
          colors = c("gold3", "blue4", "darkgoldenrod4"))
```
Word Cloud for 1 star reviews


* Checking the wordcloud for dominant words across low and high ratings
```{r}
#Ratings of 4 and above are considered as high ratings
positive_reviews <- review_tokens_by_stores %>% anti_join(custom_stopwords) %>%
                    filter (overall == 4| overall == 5) 

positive_reviews <- positive_reviews %>% dplyr::select(word)

#Ratings of 2 and below are considered as low ratings
negative_reviews <- review_tokens_by_stores %>% anti_join(custom_stopwords) %>%
                    filter (overall == 2| overall ==1 )

negative_reviews <- negative_reviews %>% dplyr::select(word)

combine_review <- c(positive_reviews,negative_reviews)

#Creating a corpus
corpus_combine = VCorpus(VectorSource(combine_review))

#Stemming the document
corpus_combine=tm_map(corpus_combine, stemDocument)
review_dtm_combine <- TermDocumentMatrix(corpus_combine)
all=as.matrix(review_dtm_combine)
colnames(all)=c("Words in high ratings","Words in low ratings")

#Creating comparison cloud
comparison.cloud(all,
 colors = c("red", "blue"),
 max.words = 100)
```

# Analyse

## Dealing with n-grams

Now, using the bag of words approach, we will get the top n-grams for both reviews and store descriptions.

* Unigrams of reviews
```{r}
#Bringing the data for using in n-grams
df <- review_data_en %>% dplyr::select(company_id, store_description, overall) %>% left_join(review_data_by_stores) %>% distinct(.)

#Tokenizing into unigrams
ngram_1_review <- df %>% 
                  unnest_tokens(word, grouped_reviews, token = "ngrams", n =1) %>%
                  anti_join(custom_stopwords)

#Finding the most frequent unigrams
ngram_1_review <- ngram_1_review %>%
                  group_by(word) %>%
                  summarise(Frequency = n(),
                  Overall = round(mean(overall))) %>%
                  arrange(desc(Frequency))

#Visualizing the top frequent unigrams
df %>% unnest_tokens(word, grouped_reviews, token = "ngrams", n =1) %>%
       anti_join(custom_stopwords) %>%
       count(word, sort = TRUE) %>%
       top_n(10) %>%
       ggplot(aes(reorder(word, n), n)) +
       geom_col() +
       labs(title="Top 10 Unigram frequency for Reviews",
       y = "Frequency",
       x = "Terms") +
       theme(plot.title = element_text(hjust = 0.5)) +
       coord_flip()

#Visualizing the top frequent unigrams by ratings
ngram_1_review %>% group_by(Overall) %>%  
                   slice_max(Frequency, n = 10) %>% 
                   ungroup() %>%
                   ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
                   geom_col(show.legend = FALSE) +
                   facet_wrap(~ Overall, ncol = 2, scales = "free") +
                   labs(title="Top 10 Unigram frequency for Reviews by Overall",
                   y = "Average Rating",
                   x = "Frequency") +
                   theme(plot.title = element_text(hjust = 0.5))


```

* Bigrams of reviews
```{r}
#Adding stop words specifically for bigrams
bi_custom_words <- c("class", "please", "job", "shop", "hand", "friend", "date", "service", "review", "product", "customer", "day", "days", "received", "money", "week", "buy", "company", "phone", "don", "ve", "ofcom", "ninja", "moonfruit", "cancelled", "virgin", "told", "people", "arrived", "paul", "av", "ben", "josh", "andy", "tom", "richer", "plugin", "amp", "hifi", "aquiss", "sounds", "controller", "zoltan", "ian", "idnet", "glue", "proxy", "helen", "eno", "oled", "sypwai", "george", "peter", "panamoz", "pine", "dotsquares", "laura", "vape", "amiga", "biz", "technoworld", "proxies", "recommend", "fast", "machine", "avoid", "fridge", "freezer", "sb", "trust", "pilot", "pc")

tibble(word = bi_custom_words,lexicon = rep("custom",length(bi_custom_words))) %>% bind_rows(stop_words) -> bi_custom_stopwords

#Bringing the data
ngram_2_review <- df %>%
                  unnest_tokens(word, grouped_reviews, token = "ngrams", n =2)

#Tokenizing for bigrams
ngram_2_review$index <- seq.int(nrow(ngram_2_review))

df2 <- ngram_2_review %>%
       separate(word, c("word1", "word2"), sep = " ") %>%
       dplyr::select('index', 'word1','word2')

ngram_2_review <- left_join(ngram_2_review, df2, by = "index")
rm(df2)

ngram_2_review <- ngram_2_review %>%
                  filter(!word1 %in% bi_custom_stopwords$word) %>%
                  filter(!word2 %in% bi_custom_stopwords$word)

ngram_2_review_splitted <- ngram_2_review %>% 
                  count(word1, word2, sort = TRUE)

#Finding the frequencies of the bigrams
ngram_2_review_combined <- ngram_2_review %>%
                  group_by(word) %>%
                  summarise(Frequency = n(),
                            Overall = round(mean(overall))) %>%
                  arrange(desc(Frequency)) %>%
                  na.omit()

#Visualizing the top frequent bigrams
ngram_2_review_combined %>% slice_max(Frequency, n = 8) %>%
                   ggplot(aes(reorder(word, Frequency), Frequency)) +
                   geom_col() +
                   labs(title="Top 10 Bigram Frequency for Reviews",
                   y = "Frequency",
                   x = "Terms") +
                   theme(plot.title = element_text(hjust = 0.5)) +
                   coord_flip()

#Visualizing the top frequent bigrams by ratings
ngram_2_review_combined %>% group_by(Overall) %>%  
                   slice_max(Frequency, n = 8) %>% 
                   ungroup() %>%
                   ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
                   geom_col(show.legend = FALSE) +
                   facet_wrap(~ Overall, ncol = 2, scales = "free") +
                   labs(title="Top 10 Bigram frequency for Reviews by Overall",
                   y = "Terms",
                   x = "Frequency") +
                   theme(plot.title = element_text(hjust = 0.5))

#Common bigrams in reviews
ngram_2_graph <- ngram_2_review_splitted %>%
                 filter(n > 60) %>%
                 graph_from_data_frame()


set.seed(321)
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(ngram_2_graph, layout = "fr") +
       geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                          arrow = a, end_cap = circle(.07, 'inches')) +
       geom_node_point(color = "lightblue", size = 3) +
       geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
       theme_void()
```

* Trigrams of reviews
```{r}
#Adding stop words specifically for bigrams
tri_custom_words <- c("class", "please", "job", "service", "shop", "hand", "friend", "date", "review", "product", "customer", "day", "days", "money", "week", "buy", "company", "phone", "don", "ve", "ofcom", "ninja", "moonfruit", "virgin", "told", "people", "arrived", "paul", "av", "ben", "josh", "andy", "tom", "richer", "plugin", "amp", "hifi", "aquiss", "sounds", "zoltan", "ian", "idnet", "glue", "proxy", "helen", "eno", "oled", "sypwai", "george", "peter", "panamoz", "pine", "dotsquares", "laura", "vape", "amiga", "biz", "technoworld", "fridge", "freezer", "iphone", "pro", "trust", "pilot", "st", "uber", "reviews", "boots", "sh", "london", "british", "xl", "ms", "avern", "pm", "june", "bullguard")

tibble(word = tri_custom_words,lexicon = rep("custom",length(tri_custom_words))) %>% bind_rows(stop_words) -> tri_custom_stopwords

#Bringing the data
ngram_3_review <- df %>% 
                  unnest_tokens(word, grouped_reviews, token = "ngrams", n =3)

#Tokenizing into trigrams
ngram_3_review$index <- seq.int(nrow(ngram_3_review))

df3 <- ngram_3_review %>%
       separate(word, c("word1", "word2", "word3"), sep = " ") %>%
       dplyr::select('index', 'word1','word2', 'word3')

ngram_3_review <- left_join(ngram_3_review, df3, by = "index")
rm(df3)

ngram_3_review <- ngram_3_review %>%
                  filter(!word1 %in% tri_custom_stopwords$word) %>%
                  filter(!word2 %in% tri_custom_stopwords$word) %>%
                  filter(!word3 %in% tri_custom_stopwords$word)

ngram_3_review_splitted <- ngram_3_review %>% 
                  count(word1, word2, word3, sort = TRUE)

#Finding the frequencies
ngram_3_review <- ngram_3_review %>%
                  group_by(word) %>%
                  summarise(Frequency = n(),
                            Overall = round(mean(overall))) %>%
                  arrange(desc(Frequency)) %>%
                  na.omit()

#Visualizing the top frequent trigrams
ngram_3_review %>% slice_max(Frequency, n = 10) %>%
                   ggplot(aes(reorder(word, Frequency), Frequency)) +
                   geom_col() +
                   labs(title="Top 10 Trigram Frequency for Reviews",
                   y = "Frequency",
                   x = "Terms") +
                   theme(plot.title = element_text(hjust = 0.5)) +
                   coord_flip()

#Visualizing the top frequent trigrams by ratings
ngram_3_review %>% group_by(Overall) %>%  
                 slice_max(Frequency, n = 7) %>% 
                 ungroup() %>%
                 ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
                 geom_col(show.legend = FALSE) +
                 facet_wrap(~ Overall, ncol = 2, scales = "free") +
                 labs(title="Top 10 Trigram frequency for Reviews by Overall",
                 y = "Terms",
                 x = "Frequency") +
                 theme(plot.title = element_text(hjust = 0.5))

#Common bigrams in reviews
ngram_3_graph <- ngram_3_review_splitted %>%
                 filter(n > 6) %>%
                 graph_from_data_frame()

set.seed(321)
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(ngram_3_graph, layout = "fr") +
       geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                          arrow = a, end_cap = circle(.07, 'inches')) +
       geom_node_point(color = "lightblue", size = 3) +
       geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
       theme_void()


```

* Unigrams of store description
```{r}
#Adding special stop words
custom_words_desc <- c("uk", "company", "customer", "business", "na", "mobile", "provide", "product", "facebook", "sony", "ireland", "tv", "computer", "phone", "oven", "laskys", "moonfruit", "cooper", "goldmanlife", "airwave", "imendmacs", "north", "battery", "lcd", "tnp", "mo", "tablet", "sellmyiphone", "iphonererecycler", "iphonerecycler", "st", "sia", "toshiba", "sonos", "nokia", "plusnet", "plasma", "virgin", "adapter")

tibble(word = custom_words_desc,lexicon = rep("custom",length(custom_words_desc))) %>% bind_rows(stop_words) -> custom_stopwords_desc

#Bringing the data for using in n-grams
df <- review_data_en %>% dplyr::select(company_id, store_description, overall) %>% left_join(review_data_by_stores) %>% distinct(.)

#Tokenizing into unigrams
ngram_1_desc <- df %>% 
                unnest_tokens(word, store_description, token = "ngrams", n =1) %>%
                anti_join(custom_stopwords_desc)

#Finding the most frequent unigrams
ngram_1_desc <- ngram_1_desc %>%
 group_by(word) %>%
 summarise(Frequency = n(),
           Overall = round(mean(overall))) %>%
 arrange(desc(Frequency))

#Visualizing the top frequent unigrams
df %>%
 unnest_tokens(word, store_description, token = "ngrams", n =1) %>%
 anti_join(custom_stopwords_desc) %>%
 count(word, sort = TRUE) %>%
 top_n(10) %>%
 ggplot(aes(reorder(word, n), n)) +
 geom_col() +
 labs(title="Top 10 Unigram frequency for Store Descriptions",
 y = "Frequency",
 x = "Terms") +
 theme(plot.title = element_text(hjust = 0.5)) +
 coord_flip()

#Visualizing the top frequent unigrams by ratings
ngram_1_desc %>%
 group_by(Overall) %>%  
 slice_max(Frequency, n = 10) %>% 
 ungroup() %>%
 ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
 geom_col(show.legend = FALSE) +
 facet_wrap(~ Overall, ncol = 2, scales = "free") +
 labs(title="Top 10 Unigram frequency for Store Descriptions by Overall",
 y = "Average Rating",
 x = "Frequency") +
 theme(plot.title = element_text(hjust = 0.5))
```
* Bigrams of store description
```{r}
#Adding special stop words
custom_words_desc <- c("uk", "company", "customer", "business", "na", "mobile", "provide", "product", "machine", "game", "console", "camera", "virgin", "ssl", "pc", "oven", "fridge", "freezer", "battery", "mo", "lcd", "tv", "cable", "tablet", "cable", "charger", "samsung", "sony") 

tibble(word = custom_words_desc,lexicon = rep("custom",length(custom_words_desc))) %>% bind_rows(stop_words) -> custom_stopwords_desc

#Bringing the data
ngram_2_desc <- df %>%
                unnest_tokens(word, store_description, token = "ngrams", n =2)

#Tokenizing for bigrams
ngram_2_desc$index <- seq.int(nrow(ngram_2_desc))

df2 <- ngram_2_desc %>%
           separate(word, c("word1", "word2"), sep = " ") %>%
           dplyr::select('index', 'word1','word2')

ngram_2_desc <- left_join(ngram_2_desc, df2, by = "index")

ngram_2_desc <- ngram_2_desc %>%
                filter(!word1 %in% custom_stopwords_desc$word) %>%
                filter(!word2 %in% custom_stopwords_desc$word)

ngram_2_desc_splitted <- ngram_2_desc %>% 
                  count(word1, word2, sort = TRUE) %>% na.omit()

#Finding the frequencies of the bigrams
ngram_2_desc_combined <- ngram_2_desc %>%
                group_by(word) %>%
                summarise(Frequency = n(),
                          Overall = round(mean(overall))) %>%
                arrange(desc(Frequency)) %>%
                na.omit()

#Visualizing the top frequent bigrams
ngram_2_desc_combined %>% slice_max(Frequency, n = 10) %>%
                 ggplot(aes(reorder(word, Frequency), Frequency)) +
                 geom_col() +
                 labs(title="Top 10 Bigram Frequency for Listing Descriptions",
                 y = "Frequency",
                 x = "Terms") +
                 theme(plot.title = element_text(hjust = 0.5)) +
                 coord_flip()

#VIsualizing the top frequent bigrams by ratings
ngram_2_desc_combined %>% group_by(Overall) %>%  
                 slice_max(Frequency, n = 10) %>% 
                 ungroup() %>%
                 ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
                 geom_col(show.legend = FALSE) +
                 facet_wrap(~ Overall, ncol = 2, scales = "free") +
                 labs(title="Top 10 Bigram frequency for Store Descriptions by Overall",
                 y = "Terms",
                 x = "Frequency") +
                 theme(plot.title = element_text(hjust = 0.5))

#Common bigrams in reviews
ngram_2_graph <- ngram_2_desc_splitted %>%
                 filter(n > 4) %>%
                 graph_from_data_frame()

set.seed(2017)
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(ngram_2_graph, layout = "fr") +
       geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                          arrow = a, end_cap = circle(.07, 'inches')) +
       geom_node_point(color = "lightblue", size = 3) +
       geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
       theme_void()

```
* Trigrams of store description
```{r}
#Adding special stop words
custom_words_desc3 <- c("uk", "company", "customer", "business", "na", "mobile", "provide", "product", "machine", "game", "console", "camera", "virgin", "ssl", "pc", "oven", "fridge", "freezer", "battery", "mo", "lcd", "tv", "cable", "tablet", "cable", "charger", "samsung", "sony")

tibble(word = custom_words_desc,lexicon = rep("custom",length(custom_words_desc))) %>% bind_rows(stop_words) -> custom_stopwords_desc3

#Bringing the data
ngram_3_desc <- df %>% 
                unnest_tokens(word, store_description, token = "ngrams", n =3)

#Tokenizing into trigrams
ngram_3_desc$index <- seq.int(nrow(ngram_3_desc))

df3 <- ngram_3_desc %>%
       separate(word, c("word1", "word2", "word3"), sep = " ") %>%
       dplyr::select('index', 'word1','word2', 'word3')

ngram_3_desc <- left_join(ngram_3_desc, df3, by = "index")
rm(df3)

ngram_3_desc <- ngram_3_desc %>%
                filter(!word1 %in% custom_stopwords_desc3$word) %>%
                filter(!word2 %in% custom_stopwords_desc3$word) %>%
                filter(!word3 %in% custom_stopwords_desc3$word)

ngram_3_desc_splitted <- ngram_3_desc %>% 
                  count(word1, word2, word3, sort = TRUE) %>% na.omit()

#Finding the frequencies
ngram_3_desc_combined <- ngram_3_desc %>%
                group_by(word) %>%
                summarise(Frequency = n(),
                          Overall = round(mean(overall))) %>%
                arrange(desc(Frequency)) %>%
                na.omit()

#Visualizing the top frequent trigrams
ngram_3_desc_combined %>% slice_max(Frequency, n = 5) %>%
                 ggplot(aes(reorder(word, Frequency), Frequency)) +
                 geom_col() +
                 labs(title="Top 10 Trigram Frequency for Store Descriptions",
                 y = "Frequency",
                 x = "Terms") +
                 theme(plot.title = element_text(hjust = 0.5)) +
                 coord_flip()

#Visualizing the top frequent trigrams by ratings
ngram_3_desc_combined %>% group_by(Overall) %>%  
                 slice_max(Frequency, n = 5) %>% 
                 ungroup() %>%
                 ggplot(aes(Frequency, fct_reorder(word, Frequency), fill = Overall)) +
                 geom_col(show.legend = FALSE) +
                 facet_wrap(~ Overall, ncol = 2, scales = "free") +
                 labs(title="Top 10 Trigram frequency for Store Descriptions by Overall",
                 y = "Terms",
                 x = "Frequency") +
                 theme(plot.title = element_text(hjust = 0.5))

ngram_3_graph <- ngram_3_desc_splitted %>%
                 filter(n > 1) %>%
                 graph_from_data_frame()

set.seed(2017)
a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(ngram_3_graph, layout = "fr") +
       geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                          arrow = a, end_cap = circle(.07, 'inches')) +
       geom_node_point(color = "lightblue", size = 3) +
       geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
       theme_void()


```

* Word Associations

Now that we have looked at the n-grams, we will try to examine some important words and look at the word associations to get a sense of what reviewers are saying

```{r}
#Casting a Document Term Matrix
dtm_1_review <- df %>%
                unnest_tokens(word, grouped_reviews, token = "ngrams", n =1) %>%
                anti_join(custom_stopwords) %>%
                count(company_id, word) %>%
                cast_dtm(company_id, word, n)

inspect(dtm_1_review)

#Checking which words correlate with "recommend"
findAssocs(dtm_1_review,"recommended",corlimit = 0.7)
findAssocs(dtm_1_review,"excellent",corlimit = 0.6)
findAssocs(dtm_1_review,"easy",corlimit = 0.4)
findAssocs(dtm_1_review,"price",corlimit = 0.5)
findAssocs(dtm_1_review,"time",corlimit = 0.4)
findAssocs(dtm_1_review,"helpful",corlimit = 0.6)
findAssocs(dtm_1_review,"support",corlimit = 0.5)

# To check and confirm what word combinations have recommended to get an idea about things which are recommended in the reviews by the user
ngram_3_review %>% group_by(word) %>%
                   count(sort = TRUE) %>%
                   filter(stringr::str_detect(word,"recommend | recommended"))
ngram_2_review %>% group_by(word) %>%
                   count(sort = TRUE) %>%
                   filter(stringr::str_detect(word,"excellent"))
ngram_2_review %>% group_by(word) %>%
                   count(sort = TRUE) %>%
                   filter(stringr::str_detect(word,"easy | time"))
```

## Correlation between ratings and metadata

We are now going to investigate if there are different sets of words that come up depending on the metadata available.

* Checking for correlation between ratings and review_lengths
```{r}
#Finding the review lengths
corr_data_1 <- review_data %>%
               mutate(review_length = str_count(reviewText)) %>%
               group_by(company_id) %>%
               mutate(average_review_length = mean(review_length),
                      mean_overall = mean(overall)) %>%
               ungroup()
#Plotting 
corr_data_1 %>% ggplot(aes(x=average_review_length,
                           y=log(mean_overall))) +
                geom_point(alpha=0.2) +
                geom_smooth(method="lm") +
                ggtitle("Rating scores vs length of reviews")

#Performing correlation test
cor.test(corr_data_1$mean_overall,
         corr_data_1$average_review_length,
         method="pearson")
```
The correlation test shows that there is a negative correlation between the ratings and review lengths. It seems that the reviews with lower ratings tend to be longer.


* Checking for correlation between ratings and country
```{r}
#Finding top 15 countries with highest reviews
top_15_country <- review_data %>%
                  mutate(country = as.factor(country)) %>%
                  group_by(country) %>%
                  summarise(mean_rating = log(mean(reviewer_rating)),
                            frequency = n()) %>%
                  slice_max(frequency, n = 15)

#Plotting 
top_15_country %>% ggplot(aes(x = fct_reorder(country, mean_rating),
                              y = mean_rating, fill = country)) +
                   geom_col() +
                   ggtitle("Rating scores vs Country of Reviewer")
```
We took the top 15 countries based on the number of reviews to see if there exists any correlation between the location and ratings. We have identified the countries where the ratings seem to be much better than the others

* Word importance by metadata

We will now look for words that come up by country

```{r} 
top_country <- review_data_en %>% 
  dplyr::select(company_id,country) %>%
  unique(.) %>% 
  group_by(country) %>% 
  summarise(total =n()) %>% 
  arrange(desc(total)) %>%
  top_n(10)

top_tokenized_country <- review_data_en %>% 
  dplyr::select(company_id,country) %>% 
  filter(country %in% top_country$country) %>% 
  unique(.)

country_tokens <- review_tokens_by_stores %>% 
  right_join(top_tokenized_country) %>% group_by(country,word) %>% 
  summarise(total=sum(n)) %>% 
  arrange(desc(total)) 

output_country <- data.frame()
for(countries in 1:nrow(top_country)){
  print(paste0("For year: ",top_country$country[countries]))
  
  output <- country_tokens %>% ungroup() %>% filter(country == top_country$country[countries]) %>% top_n(10,total) %>% dplyr::select(-total) %>% mutate(rank = row_number())
  output_country <- rbind(output_country, output)
}

output_country %>% group_by(country) %>%
                   slice_max(rank, n = 10) %>%
                   ungroup() %>%
                   ggplot(aes(rank, fct_reorder(word, rank), fill = country)) +
                   geom_col(show.legend = FALSE) +
                   facet_wrap(~ country, ncol = 5, scales = "free") +
                   labs(title="Top 10 Unigrams by Country",
                   y = "Term",
                   x = "Rank") +
                   theme(plot.title = element_text(hjust = 0.5))
```

We also try to see what word are becoming more important over the years.

```{r}
top_year <- review_data_en %>% 
  dplyr::select(company_id,year) %>%
  unique(.) %>% 
  group_by(year) %>% 
  summarise(total =n()) %>% 
  arrange(desc(total))

top_tokenized_year <- review_data_en %>% 
  dplyr::select(company_id,year) %>% 
  filter(year %in% top_year$year) %>% 
  unique(.)

year_tokens <- review_tokens_by_stores %>% 
  right_join(top_tokenized_year) %>% group_by(year,word) %>% 
  summarise(total=sum(n)) %>% 
  arrange(desc(total)) 

output_year <- data.frame()
for(years in 1:nrow(top_year)){
  print(paste0("For year: ",top_year$year[years]))
  
  output1 <- year_tokens %>% ungroup() %>% filter(year == top_year$year[years]) %>% top_n(10,total) %>% dplyr::select(-total) %>% mutate(rank = row_number())
  output_year <- rbind(output_year, output1)
}

output_year %>% group_by(year) %>%
                   slice_max(rank, n = 10) %>%
                   ungroup() %>%
                   ggplot(aes(rank, fct_reorder(word, rank), fill = year)) +
                   geom_col(show.legend = FALSE) +
                   facet_wrap(~ year, ncol = 5, scales = "free") +
                   labs(title="Top 10 Unigrams by Years",
                   y = "Term",
                   x = "Rank") +
                   theme(plot.title = element_text(hjust = 0.5))

```


# Part B

In this section, we will perform sentiment analysis and feature extraction from the reviews

We will start off by finding some text features and connecting them with the target variable. This will be done through regression models. We will compare the models to find which features have significant effect on the target variable.

Next, we will examine the text metrics to evaluate the effects on the target. The readability, formality, diversity, polarity and review length metrics will be utilized.

Then, we will try to understand the sentiments of the texts. Using the analysed sentiments, we will find the best fit sentiment dictionary for this dataset. 

Finally, we will combine the sentiments with some syntactic features to predict the target variable as well. 

* Loading the relevant libraries for this section

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center")
library(qdap)
library(tidytext)
library(tidyverse)
library(readr)
library(tm)
library(qdap)
library(textclean)
library(wordcloud)
library(reshape2)
library(stringi)
library(textstem)
library(sentimentr)
library(lexicon)
library(FSelector)
library(future.apply)
library(rJava)
#install.packages('egg')
library(egg)
library(stargazer)
library(MASS)
library(caret)
library(magrittr)
#install.packages('ordinal')
library(ordinal)
library(data.table)
#install.packages('textdata')
library(textdata)
library(hunspell)
```

# Ingest

* Dataset preparation

We will use the prepared dataset from the previous section.

```{r}
#Importing the dataset
dataset <- readRDS("review_data_en.rds")
dataset_stores <- readRDS("review_data_by_stores.rds")
```

```{r}
#Setting the correct datatype of the target variable
dataset$reviewer_rating <- as.numeric(dataset$reviewer_rating)
dataset$overall <- as.numeric(dataset$overall)
```

# Process

* Text cleaning

Applying some additional text cleaning relevant for the analysis of this section.

```{r}
#Getting sample reviews to understand the required cleaning
#dataset$reviewText %>%sample(100)%>% check_text(n=1)

#Cleaning the reviews
dataset$reviewText <- replace_emoticon(dataset$reviewText) #convert emoticons to words
dataset$reviewText <- replace_emoji(dataset$reviewText) #convert emojis to words
dataset$reviewText <- replace_incomplete(dataset$reviewText) #dealing with incomplete sentences
dataset$reviewText <- add_missing_endmark(dataset$reviewText) #putting required endmarks
dataset$reviewText <- textshape::split_sentence(dataset$reviewText)
dataset$reviewText <- replace_non_ascii(dataset$reviewText) #replacing common non-ascii words
dataset$reviewText <- gsub("[ |\t]+", " ", dataset$reviewText) #removing white space
```

* Getting the tokenized reviews at both store and review level
```{r}
#Using selective stop words from part A
custom_words <- c("class", "job", "shop", "hand", "friend", "date", "service", "review", "product", "customer", "day", "days", "received", "money", "week", "buy", "company", "phone", "don", "ve", "ofcom", "ninja", "moonfruit", "cancelled", "virgin", "told", "people", "arrived", "paul", "av", "ben", "josh", "andy", "tom", "richer", "plugin", "amp", "hifi", "aquiss", "sounds", "controller", "zoltan", "ian", "idnet", "glue", "proxy", "helen", "eno", "oled", "sypwai", "george", "peter", "panamoz", "pine", "dotsquares", "laura", "vape", "amiga", "biz", "technoworld", "proxies")

#Binding them with the default stop word dictionary
tibble(word = custom_words,lexicon = rep("custom",length(custom_words))) %>% bind_rows(stop_words) -> custom_stopwords

#Tokenizing the reviews at store level
tokens_all <- dataset_stores %>% 
              unnest_tokens(word,grouped_reviews) %>% 
              count(word,company_id) %>% 
              anti_join(custom_stopwords) 

#Tokenizing the reviews at review level
tokens_all_review <- dataset %>% 
              unnest_tokens(word,reviewText) %>% 
              count(word,review_id) %>% 
              anti_join(custom_stopwords)

count <- tokens_all_review %>% group_by(review_id) %>% summarise(wordcount = n())

tokens_all_review <- tokens_all_review %>% left_join(count)
```

# Analyse

## Feature Extraction

* Finding the features to extract
```{r}
#Getting the average ratings for each store for rating categorizing
rating_categories <- dataset %>% 
  group_by(company_id) %>% 
  summarise(avg_rating = mean(reviewer_rating)) %>%
  ungroup()

#Finding the levels to aggregate the words 
quantile(rating_categories$avg_rating)

#Assigning ratings to two categories
rating_categories$rating_category <- ifelse(rating_categories$avg_rating < 4.2, 1, 2)

ratings_categories_tokens <- tokens_all %>% left_join(rating_categories) %>% 
  group_by(rating_category,word) %>% summarise(total =sum(n))
  
#Looking at potential features to extract
ratings_categories_tokens %>% filter(rating_category == 1) %>% arrange(desc(total)) %>% top_n(10)

ratings_categories_tokens %>% filter(rating_category == 2) %>% arrange(desc(total)) %>% top_n(10)
```

* Extracting features from text and creating regression models 

From the previous output, we will now select some words as features and explore the regressions.

We have formatted the features are binary values in the code. Hence, we will use polr function to perform logistical regression as the appropriate method.

```{r}
reviews_for_feature <- dataset %>% dplyr::select(review_id, reviewText, store_description, reviewer_rating, overall)
reviews_for_feature$reviewText <- tolower(reviews_for_feature$reviewText)
reviews_for_feature$store_description <- tolower(reviews_for_feature$store_description)

#Finding reviews that contain "delivery"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "delivery"))) %>%
 mutate(delivery=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,delivery) -> delivery_feature

delivery_feature_final <- delivery_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, delivery)
model_delivery <- polr(factor(reviewer_rating) ~ delivery, data=delivery_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain "time"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "time"))) %>%
 mutate(time=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,time) -> time_feature

time_feature_final <- time_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, time)
model_time <- polr(factor(reviewer_rating) ~ time, data=time_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain "price"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "price"))) %>%
 mutate(price=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,price) -> price_feature

price_feature_final <- price_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, price)
model_price <- polr(factor(reviewer_rating) ~ price, data=price_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain "helpful"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "helpful"))) %>%
 mutate(helpful=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,helpful) -> helpful_feature

helpful_feature_final <- helpful_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, helpful)
model_helpful <- polr(factor(reviewer_rating) ~ helpful, data=helpful_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain "easy"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "easy"))) %>%
 mutate(easy=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,easy) -> easy_feature

easy_feature_final <- easy_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, easy)
model_easy <- polr(factor(reviewer_rating) ~ easy, data=easy_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain "excellent"
reviews_for_feature %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "excellent"))) %>%
 mutate(excellent=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,excellent) -> excellent_feature

excellent_feature_final <- excellent_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, excellent)
model_excellent <- polr(factor(reviewer_rating) ~ excellent, data=excellent_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain upper case letter
dataset %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(reviewText, "\\b[A-Z]+\\b"))) %>%
 mutate(upper_case=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,upper_case) -> upper_case_feature

upper_case_feature_final <- upper_case_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, upper_case)
model_upper <- polr(factor(reviewer_rating) ~ upper_case, data=upper_case_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that have email
dataset %>% group_by(review_id) %>%
  summarise(TF=sum(str_detect(email, "  "))) %>%
  mutate(emails=ifelse(TF>0, "0", "1")) %>%
 dplyr::select(review_id,emails) -> email_feature

email_feature_final <- email_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, emails)
model_email <- polr(factor(reviewer_rating) ~ emails, data=email_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that have phone number
dataset %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(phone_number, "  "))) %>%
 mutate(phone=ifelse(TF>0, "0", "1")) %>%
 dplyr::select(review_id,phone) -> phone_feature

phone_feature_final <- phone_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, phone)
model_phone <- polr(factor(reviewer_rating) ~ phone, data=phone_feature_final, Hess=TRUE, method = c("logistic"))

#Finding reviews that contain exclamations
dataset %>% group_by(review_id) %>%
 summarise(TF=sum(str_detect(review, "!"))) %>%
 mutate(exclm=ifelse(TF>0, "1", "0")) %>%
 dplyr::select(review_id,exclm) -> exclm_feature

exclm_feature_final <- exclm_feature %>%
 inner_join(dataset) %>%
 dplyr::select(review_id, reviewer_rating, exclm)
model_exclm <- polr(factor(reviewer_rating) ~ exclm, data=exclm_feature_final, Hess=TRUE, method = c("logistic"))

#Comparing all the feature models
stargazer::stargazer(model_delivery, model_time, model_upper, model_easy, model_excellent, model_exclm, model_helpful, model_price, model_phone, model_email, 
                     type = "text", add.lines = list(c("AIC", round(AIC(model_delivery),1),
                                                              round(AIC(model_time),1),
                                                              round(AIC(model_upper),1),
                                                              round(AIC(model_easy),1),
                                                              round(AIC(model_excellent),1),
                                                              round(AIC(model_helpful),1),
                                                              round(AIC(model_price),1),
                                                              round(AIC(model_email),1),
                                                              round(AIC(model_exclm),1),
                                                              round(AIC(model_phone),1))),
                     out = "features.txt", single.row = T, align = T, flip = T)
```
The outcome of the analysis shows that each of the features are significant to predict the target variable and have a high AIC value. 

# Finding the effects of each feature on ratings

Now, we use all the features together to create a regression model to predict the target variable.

```{r}
#Combining all features into a data.frame
review_feature_final <- reviews_for_feature %>%
                        left_join(delivery_feature) %>%
                        left_join(time_feature) %>%
                        left_join(upper_case_feature)%>%
                        left_join(easy_feature)%>%
                        left_join(excellent_feature)%>%
                        left_join(helpful_feature)%>%
                        left_join(price_feature)%>%
                        left_join(email_feature)%>%
                        left_join(phone_feature)%>%
                        left_join(exclm_feature)

#Creating a backup
#saveRDS(review_feature_final,"review_feature_final.rds")

#Conducting regression with all the features
regress_all_features <- review_feature_final %>% dplyr::select(,-c(review_id, reviewText, store_description, overall))
model_features_all <- polr(factor(reviewer_rating) ~ ., data = regress_all_features)
```

## Text Metrics Analysis

Here, we will analyse the readability, formality, polarity, diversity and review lengths of both the reviews and the store descriptions.

* Checking if readability of reviews has effect on ratings

```{r eval=FALSE}
all_review <- dataset %>% dplyr::select(review_id, reviewText, reviewer_rating) %>% unique(.)

readability_all_review <- data.frame()

for(i in 1:nrow(all_review)){
  
  readability <- data.frame() 
  
  desc <- iconv(all_review$reviewText[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(readability <- flesch_kincaid(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(readability$Readability)){
  
     readability <- readability$Readability
     readability$review_id <- all_review$review_id[i]
     readability_all_review <- bind_rows(readability_all_review,readability) 
   }
  
  print(i)
}
```
```{r eval=FALSE}
#Adding readability output to dataset
dataset %>% left_join(readability_all_review) -> dataset_read_review

readability_review_plot <- dataset_read_review %>% group_by(review_id) %>%
  dplyr::select(FK_grd.lvl, reviewer_rating) %>% 
  na.omit() %>% 
  ggplot(aes(x = FK_grd.lvl,y = log(reviewer_rating))) +
  geom_smooth(method="lm") +
  geom_point() +
  ggtitle("Overall vs Readability of Reviews")
#ggsave("readability_review_plot.png")

#Plotting the relation between the readability of the store description and the rating scores
cor.test(dataset_read_review$reviewer_rating,
 dataset_read_review$FK_grd.lvl,
 method="pearson")
```



* Checking the formality of the reviews
```{r eval=FALSE}
formality_all_review <- data.frame()

for(i in 1:nrow(all_review)){
  
  formality <- data.frame() 
  
  desc <- iconv(all_review$reviewText[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(formality <- formality(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(formality$formality)){
  
     formality <- formality$formality
     formality$review_id <- all_review$review_id[i]
     formality_all_review <- bind_rows(formality_all_review,formality) 
   }
  
  print(i)
}

#saveRDS(formality_all_review, "formality_all_review.rds")
```
```{r eval=FALSE}
formality_all_review <- read_rds("formality_all_review.rds")
#Adding formality output to dataset
dataset_read_review %>% left_join(formality_all_review) -> dataset_read_review

formality_review_plot <- dataset_read_review %>% group_by(review_id) %>%
  dplyr::select(formality, reviewer_rating) %>% 
  na.omit() %>% 
  ggplot(aes(x=formality,y=reviewer_rating))+geom_smooth(method="lm")+geom_point()
#ggsave("formality_review_plot.png")
```



* Checking the polarity of the reviews
```{r eval=FALSE}
polarity_all_review <- data.frame()

for(i in 1:nrow(all_review)){
  
  polarity <- data.frame() 
  
  desc <- iconv(all_review$reviewText[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(polarity <- polarity(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(polarity$all)){
  
     polarity <- polarity$all
     polarity$review_id <- all_review$review_id[i]
     polarity_all_review <- bind_rows(polarity_all_review,polarity) 
   }
  
  print(i)
}
```
```{r eval=FALSE}
#Adding polarity output to dataset
dataset_read_review %>% left_join(polarity_all_review) -> dataset_read_review

polarity_review_plot <- dataset_read_review %>% group_by(review_id) %>%
  dplyr::select(polarity, reviewer_rating) %>% 
  na.omit() %>% 
  ggplot(aes(x = polarity,y = reviewer_rating)) + geom_smooth(method="lm") + geom_point() + ylim(-1,6)
#ggsave("polarity_review_plot.png")
```



* Checking for the diversity of the reviews against ratings
```{r eval=FALSE}
diversity_review <- qdap::diversity(all_review$reviewText,all_review$review_id)
diversity_review$review_id <- as.numeric(diversity_review$review_id)

#Adding polarity output to dataset
dataset_read_review %>% left_join(diversity_review) -> dataset_read_review

shannon_review_plot <- dataset_read_review %>% group_by(review_id) %>%
  dplyr::select(shannon, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = shannon,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("shannon_review_plot.png")

simpson_review_plot <- dataset_read_review %>% group_by(company_id) %>%
  dplyr::select(simpson, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = simpson,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("simpson_review_plot.png")

berger_parker_review_plot <- dataset_read_review %>% group_by(company_id) %>%
  dplyr::select(berger_parker, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = berger_parker,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("berger_parker_review_plot.png")

collision_review_plot <-dataset_read_review %>% group_by(company_id) %>%
  dplyr::select(collision, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = collision,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("collision_review_plot.png")

brillouin_review_plot <- dataset_read_review %>% group_by(company_id) %>%
  dplyr::select(brillouin, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = brillouin,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("brilouin_review_plot.png")
```

* Regressing the readability, formality, polarity and wordcount of reviews against overall
```{r eval=FALSE}
dataset_read_review
model1 <- polr(factor(reviewer_rating) ~ FK_grd.lvl, data = na.omit(dataset_read_review))
model2 <- polr(factor(reviewer_rating) ~ formality, data = na.omit(dataset_read_review))
model3 <- polr(factor(reviewer_rating) ~ polarity, data = na.omit(dataset_read_review))
model4 <- polr(factor(reviewer_rating) ~ shannon, data = na.omit(dataset_read_review))
model5 <- polr(factor(reviewer_rating) ~ simpson, data = na.omit(dataset_read_review))
model6 <- polr(factor(reviewer_rating) ~ collision, data = na.omit(dataset_read_review))
model7 <- polr(factor(reviewer_rating) ~ brillouin, data = na.omit(dataset_read_review))
model8 <- polr(factor(reviewer_rating) ~ berger_parker, data = na.omit(dataset_read_review))

stargazer::stargazer(model1,model2,model3,model4,model5,model6,model7,model8,type = "text",
                     add.lines = list(c("AIC", round(AIC(model1),1),
                                               round(AIC(model2),1),
                                               round(AIC(model3),1),
                                               round(AIC(model4),1),
                                               round(AIC(model5),1),
                                               round(AIC(model6),1),
                                               round(AIC(model7),1),
                                               round(AIC(model8),1))),
                     out = "features.txt", single.row = T, align = T, flip = T)
```

* Checking to see if readability of store description has effect on ratings
```{r}
all_company <- dataset %>% dplyr::select(company_id, store_description, overall) %>% unique(.)

readability_all_desc <- data.frame()

for(i in 1:nrow(all_company)){
  
  readability <- data.frame() 
  
  desc <- iconv(all_company$store_description[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(readability <- flesch_kincaid(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(readability$Readability)){
  
     readability <- readability$Readability
     readability$company_id <- all_company$company_id[i]
     readability_all_desc <- bind_rows(readability_all_desc,readability) 
   }
  
  print(i)
}

#Adding readability output to dataset
dataset %>% left_join(readability_all_desc) -> dataset_read_desc

readability_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(FK_grd.lvl, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = FK_grd.lvl,y = overall)) +
  geom_smooth(method="lm") +
  geom_point() +
  ggtitle("Overall vs Readability of Store Description")
ggsave("readability_desc_plot.png")

#Plotting the relation between the readability of the store description and the rating scores
cor.test(dataset_read_desc$overall,
 dataset_read_desc$FK_grd.lvl,
 method="pearson")
```

* Checking to see if formality of store description has effect on ratings

```{r}
formality_all_desc <- data.frame()

for(i in 1:nrow(all_company)){
  
  formality <- data.frame() 
  
  desc <- iconv(all_company$store_description[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(formality <- formality(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(formality$formality)){
  
     formality <- formality$formality
     formality$company_id <- all_company$company_id[i]
     formality_all_desc <- bind_rows(formality_all_desc,formality) 
   }
  
  print(i)
}

#Adding formality output to dataset
dataset_read_desc %>% left_join(formality_all_desc) -> dataset_read_desc

formality_desc_plot <- formality_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(formality, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x=formality,y=overall))+geom_smooth(method="lm")+geom_point()
ggsave("formality_desc_plot.png")

#Plotting the relation between the formality of the store description and the rating scores
cor.test(dataset_read_desc$overall,
 dataset_read_desc$formality,
 method="pearson")
```

* Checking to see if polarity of store description has effect on ratings

```{r}
polarity_all_desc <- data.frame()

for(i in 1:nrow(all_company)){
  
  polarity <- data.frame() 
  
  desc <- iconv(all_company$store_description[i])
  desc <- removeNumbers(desc)
  desc <- removePunctuation(desc)

  tryCatch(polarity <- polarity(desc),error=function(e){
    cat("Error parsing")
  })
    
  if(!is.null(polarity$all)){
  
     polarity <- polarity$all
     polarity$company_id <- all_company$company_id[i]
     polarity_all_desc <- bind_rows(polarity_all_desc,polarity) 
   }
  
  print(i)
}

#Adding polarity output to dataset
dataset_read_desc %>% left_join(polarity_all_desc) -> dataset_read_desc

polarity_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(polarity, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = polarity,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("polarity_desc_plot.png")

#Plotting the relation between the polarity of the store description and the rating scores
cor.test(dataset_read_desc$overall,
 dataset_read_desc$polarity,
 method="pearson")
```

* Checking to see if diversity of store description has effect on ratings

```{r}
diversity_desc <- qdap::diversity(all_company$store_description,all_company$company_id)
diversity_desc$company_id <- as.numeric(diversity_desc$company_id)

#Adding diversity output to dataset
dataset_read_desc %>% left_join(diversity_desc) -> dataset_read_desc

shannon_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(shannon, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = shannon,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("shannon_desc_plot.png")

simpson_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(simpson, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = simpson,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("simpson_desc_plot.png")

berger_parker_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(berger_parker, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = berger_parker,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("berger_parker_desc_plot.png")

collision_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(collision, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = collision,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("collision_desc_plot.png")

brillouin_desc_plot <- dataset_read_desc %>% group_by(company_id) %>%
  dplyr::select(brillouin, overall) %>% 
  na.omit() %>% 
  ggplot(aes(x = brillouin,y = overall)) + geom_smooth(method="lm") + geom_point()
ggsave("brillouin_desc_plot.png")
```

* Checking to see if wordcount of store description has effect on ratings

```{r}
#Adding word count column
dataset_read_desc$wordcount = as.numeric(qdap::wc(dataset_read_desc$store_description, byrow = TRUE))

#Plotting Word Count against price
wordcount_desc_plot <- dataset_read_desc %>% dplyr::select(wordcount,overall) %>% na.omit() %>%
  ggplot(aes(x = wordcount,y = log(overall))) + geom_smooth(method = "lm") + geom_point()
ggsave("wordcount_desc_plot.png")

cor.test(dataset_read_desc$overall,
 dataset_read_desc$wordcount,
 method="pearson")
```

* Regressing the readability, formality, polarity and wordcount of store description against overall
```{r}
dataset_read_desc
model9 <- polr(factor(overall) ~ FK_grd.lvl, data = na.omit(dataset_read_desc))
model10 <- polr(factor(overall) ~ formality, data = na.omit(dataset_read_desc))
model11 <- polr(factor(overall) ~ polarity, data = na.omit(dataset_read_desc))
model12 <- polr(factor(overall) ~ shannon, data = na.omit(dataset_read_desc))
model13 <- polr(factor(overall) ~ simpson, data = na.omit(dataset_read_desc))
model14 <- polr(factor(overall) ~ collision, data = na.omit(dataset_read_desc))
model15 <- polr(factor(overall) ~ brillouin, data = na.omit(dataset_read_desc))
model16 <- polr(factor(overall) ~ berger_parker, data = na.omit(dataset_read_desc))

stargazer::stargazer(model9,model10,model11,model12,model13,model14,model15,model16,type = "text",
                     add.lines = list(c("AIC", round(AIC(model9),1),
                                               round(AIC(model10),1),
                                               round(AIC(model11),1),
                                               round(AIC(model12),1),
                                               round(AIC(model13),1),
                                               round(AIC(model14),1),
                                               round(AIC(model15),1),
                                               round(AIC(model16),1))),
                     out = "features.txt", single.row = T, align = T, flip = T)
```

# Sentiment Analysis

* Checking the number of positive and negative sentiments of reviews 

We will start off by importing different dictionaries and getting the number of positive and negative sentiments of each

```{r}
#Check afinn
#get_afinn <- get_sentiments("afinn")
#saveRDS(get_afinn, "get_afinn.rds")
get_afinn <- readRDS("get_afinn.rds")
afinn<- inner_join(tokens_all_review, get_afinn)

afinn$sentiment<-ifelse(afinn$value>0,"positive",ifelse(afinn$value<0,"negative","neutral"))

afinnsentiments = afinn %>%
  group_by(review_id,sentiment) %>% 
  summarise(total=n(), wordcount = mean(wordcount)) %>%
pivot_wider(names_from=sentiment, values_from=total,values_fill=list(total=0)) %>%
mutate(sentiment = (positive-negative)/(positive+negative))

afinnsentiments

#check bing 
get_bing <- readRDS("get_bing.rds")
#get_bing <- get_sentiments("bing")
bing <- inner_join(tokens_all_review,get_bing)
#saveRDS(get_bing, "get_bing.rds")

#sentiment score of bing
bingsentiments = bing %>%
  group_by(review_id,sentiment) %>%
  summarise(total=n(), wordcount = mean(wordcount)) %>%
pivot_wider(names_from=sentiment, values_from=total,values_fill=list(total=0)) %>%
mutate(sentiment = (positive-negative)/(positive+negative))

bingsentiments

#calculate sentiment score of nrc
#get_nrc <- get_sentiments("nrc")
get_nrc <- readRDS("get_nrc.rds")
nrc <- inner_join(tokens_all_review,get_nrc)
#saveRDS(get_nrc, "get_nrc.rds")

nrcsentiments = nrc%>%
  group_by(review_id,sentiment) %>%
  summarise(total=n(), wordcount = mean(wordcount)) %>%
  filter(sentiment %in% c("positive","negative")) %>%
pivot_wider(names_from=sentiment, values_from=total,values_fill=list(total=0)) %>%
mutate(sentiment = (positive-negative)/(positive+negative))

nrcsentiments

#Check loughran
#get_loughran <- get_sentiments("loughran")
get_loughran <- readRDS("get_loughran.rds")
loughran<- inner_join(tokens_all_review,get_loughran)
#saveRDS(get_loughran, "get_loughran.rds")

loughransentiments = loughran %>%
  group_by(review_id,sentiment) %>%
  summarise(total=n(), wordcount = mean(wordcount)) %>%
  filter(sentiment %in% c("positive","negative")) %>%
pivot_wider(names_from=sentiment, values_from=total,values_fill=list(total=0)) %>%
  
mutate(sentiment = (positive-negative)/(positive+negative))

loughransentiments
```

```{r}
#calculate the number of positive and negative tokens can be detected by each dictionary
afinn_1<-afinn %>%
  group_by(sentiment) %>%
  summarise(total=n())

bing_1<-bing %>%
  filter(sentiment %in% c("positive","negative")) %>%
  group_by(sentiment) %>%
  summarise(total=n())

loughran_1<-loughran%>%
  filter(sentiment %in% c("positive","negative")) %>%
  group_by(sentiment) %>%
  summarise(total=n())

nrc_1<-nrc%>%
  filter(sentiment %in% c("positive","negative")) %>%
  group_by(sentiment) %>%
  summarise(total=n())
```

```{r}
#plot the total number of positive and negative tokens respect to each dictionary
evaluation1<-data.frame(polarity=c('negative','positive'),
            afinn=afinn_1$total,
            bing=bing_1$total,
            loughran=loughran_1$total,
            nrc=nrc_1$total)
           
evaluation1<-evaluation1%>%
  pivot_longer(!polarity,names_to = "dictionary", values_to ="total")

evaluation1%>%
  group_by(dictionary,polarity)%>%
  ggplot(aes(x=dictionary,y=total))+geom_col(aes(fill=polarity),position = position_dodge2(preserve = 'single'))+geom_text(aes(label=total),position = position_dodge2(width=0.8,preserve = 'single'),vjust=-0.5,hjust=0.5)
```

*Understanding the dictionary coverages

We will try to analyse how much of the reviews are being covered by the dictionaries

```{r}
afinnsentiments_coverage<-afinnsentiments%>%
  mutate(afinn_pos_coverage=positive/wordcount*100)%>%
  mutate(afinn_neg_coverage=negative/wordcount*100)%>%
  mutate(afinn_coverage=(negative+positive)/wordcount*100)

bingsentiments_coverage<-bingsentiments%>%
  mutate(bing_pos_coverage=positive/wordcount*100)%>%
  mutate(bing_neg_coverage=negative/wordcount*100)%>%
  mutate(bing_coverage=(negative+positive)/wordcount*100)

nrcsentiments_coverage<-nrcsentiments%>%
  mutate(nrc_pos_coverage=positive/wordcount*100)%>%
  mutate(nrc_neg_coverage=negative/wordcount*100)%>%
  mutate(nrc_coverage=(negative+positive)/wordcount*100)

loughransentiments_coverage<-loughransentiments%>%
  mutate(loughran_pos_coverage=positive/wordcount*100)%>%
  mutate(loughran_neg_coverage=negative/wordcount*100)%>%
  mutate(loughran_coverage=(negative+positive)/wordcount*100)

afinn_coverage<-
  afinnsentiments_coverage%>%
  dplyr::select(review_id,afinn_pos_coverage,afinn_neg_coverage,afinn_coverage)

bing_coverage<-
  bingsentiments_coverage%>%
  dplyr::select(review_id,bing_pos_coverage,bing_neg_coverage,bing_coverage)

nrc_coverage<-
  nrcsentiments_coverage%>%
  dplyr::select(review_id,nrc_pos_coverage,nrc_neg_coverage,nrc_coverage)

loughran_coverage<-
  loughransentiments_coverage%>%
  dplyr::select(review_id,loughran_pos_coverage,loughran_neg_coverage,loughran_coverage)


all_coverage<- afinn_coverage %>% left_join(bing_coverage)
all_coverage<- all_coverage %>% left_join(nrc_coverage)
all_coverage<- all_coverage %>% left_join(loughran_coverage)

all_coverage[is.na(all_coverage)] <- 0

all_coverage<-all_coverage%>%
  dplyr::select(review_id,afinn_pos_coverage,afinn_neg_coverage,afinn_coverage,
         bing_pos_coverage,bing_neg_coverage,bing_coverage,
         nrc_pos_coverage,nrc_neg_coverage,nrc_coverage)


dictionary_coverage<-data.frame(cc='coverage',
                       afinn_pos= mean(all_coverage$afinn_pos_coverage),
                       afinn_neg= mean(all_coverage$afinn_neg_coverage),
                      # afinn= mean(All_dictionary_coverage$afinn_coverage),
                       bing_pos= mean(all_coverage$bing_pos_coverage),
                       bing_neg= mean(all_coverage$bing_neg_coverage),
                       #bing= mean(All_dictionary_coverage$bing_coverage),
                       nrc_pos= mean(all_coverage$nrc_pos_coverage),
                       nrc_neg= mean(all_coverage$nrc_neg_coverage))
                      # nrc= mean(All_dictionary_coverage$nrc_coverage)
dictionary_coverage<-dictionary_coverage%>%
  pivot_longer(!cc,names_to = "dictionary", values_to ="coverage")

dictionary_coverage
ggplot(dictionary_coverage,aes(x=dictionary,y=coverage))+geom_col(aes(fill=dictionary))+ggtitle("Coverage of Each Dictionary")
```

* Sentiment dictionary analysis for store level

We will now use regression analysis to find the best fit dictionary to predict the target variable. 

```{r}
# Getting average reviewer ratings by each stores for better relating the ratings with the curent dataset
company_id_avg_rating <- dataset %>% group_by(company_id) %>% summarise(avg_rating = round(mean(reviewer_rating)))

# Bing Liu - Sentiment Dictionary 
tokens_all %>% inner_join(get_bing) %>%
  count(sentiment,company_id) %>% spread(sentiment,n) %>%
  mutate(bing_liu_sentiment = positive-negative) %>%
  dplyr::select(company_id,bing_liu_sentiment) -> bing_liu_sentiment_company

bing_liu_sentiment_company <- bing_liu_sentiment_company %>%
  left_join(company_id_avg_rating)

# NRC Dictionary 
tokens_all %>% inner_join(get_nrc) %>% 
  count(sentiment,company_id) %>% 
  spread(sentiment,n)  -> emotions_nrc

emotions_nrc <- emotions_nrc %>% 
  left_join(company_id_avg_rating) %>% 
  mutate(sentiment_nrc = positive-negative)

# Afinn Dictionary
tokens_all %>% inner_join(get_afinn) %>% 
  group_by(company_id) %>% 
  summarise(sentiment_affin = sum(value)) -> sentiment_affin

sentiment_affin <- sentiment_affin %>% 
  left_join(company_id_avg_rating)

# Loughran Dictionary
tokens_all %>% inner_join(get_loughran) %>% 
  count(sentiment,company_id) %>% 
  spread(sentiment,n) -> sentiments_loughran

sentiments_loughran <- sentiments_loughran %>% 
  left_join(company_id_avg_rating) %>% 
  mutate(sentiment_loughran = positive-negative) %>% 
  dplyr::select(company_id,avg_rating,sentiment_loughran)

all_together_sentiments_company <- data.frame()
all_together_sentiments_company <- bing_liu_sentiment_company %>% 
  left_join(emotions_nrc) 
all_together_sentiments_company <- all_together_sentiments_company %>%
  left_join(sentiment_affin)
all_together_sentiments_company <- all_together_sentiments_company %>%
  left_join(sentiments_loughran) %>% 
  na.omit()

# Plot the sentiment
p1 <- all_together_sentiments_company %>%
        mutate(index = row_number(), sign = sign(bing_liu_sentiment)) %>%
        ggplot(aes(x=index,y=bing_liu_sentiment, fill = sign))+
        geom_bar(stat="identity")
p2 <- all_together_sentiments_company %>%
        mutate(index = row_number(), sign = sign(sentiment_nrc)) %>%
        ggplot(aes(x=index,y=sentiment_nrc, fill = sign))+
        geom_bar(stat="identity")
p3 <- all_together_sentiments_company %>%
        mutate(index = row_number(), sign = sign(sentiment_affin)) %>%
        ggplot(aes(x=index,y=sentiment_affin, fill = sign))+
        geom_bar(stat="identity")
p4 <- all_together_sentiments_company %>%
        mutate(index = row_number(), sign = sign(sentiment_loughran)) %>%
        ggplot(aes(x=index,y=sentiment_loughran, fill = sign))+
        geom_bar(stat="identity")
ggarrange(p1,p2,p3,p4)

# Bing Liu
model17 <- lm(log(avg_rating)~bing_liu_sentiment, 
             data=all_together_sentiments_company)

# NRC affection 
model18 <- lm(log(avg_rating)~sentiment_nrc,
             data=all_together_sentiments_company)

#Afinn 
model19 <- lm(log(avg_rating)~sentiment_affin,
             data=all_together_sentiments_company)
# Loughran
model20 <- lm(log(avg_rating)~sentiment_loughran, 
             data=all_together_sentiments_company)

stargazer::stargazer(model17,model18,model19,model20,type = "text")
```

# Extract feelings from NRC dictionary

The NRC dictionary provides the affection levels of the text as well. We will analyse the different affection categories and perform regression with them

```{r}
nrc_feelings <- tokens_all %>%
                inner_join(get_nrc) %>%
                count(sentiment,company_id) %>%
                spread(sentiment,n) %>%
                mutate(nrc_sentiment = (positive-negative)/(positive+negative)) %>%
                dplyr::select(-c(positive,negative)) %>%
                pivot_longer(anger:nrc_sentiment,names_to = "feeling",values_to="nrc_sentiment")

# Plot the feelings extracted
nrc_feelings %>% ggplot(aes(x=company_id,y=nrc_sentiment,fill=feeling))+
                 geom_smooth()+
                 facet_wrap(~feeling,scales="free_y",ncol=2)

#Running regressions for nrc feelings
nrc_feelings_model = nrc_feelings %>% spread(feeling, nrc_sentiment, fill = 0)
nrc_feelings_model = left_join(nrc_feelings_model, company_id_avg_rating)
nrc_feelings_model$avg_rating = as.numeric(nrc_feelings_model$avg_rating)

model21 <- lm(log(avg_rating)~.-company_id, data=nrc_feelings_model)
stargazer::stargazer(model21, type = "text")
```

# Syntactic Feature Analysis

For syntactic features, we will use exclamation marks and capital letter combine them with different sentiments in regression models.

```{r}
# Calculate the number of exclamation marks in each store
syntactical_info_excl <-  dataset %>% left_join(company_id_avg_rating) %>% 
                          left_join(all_together_sentiments_company) %>%
                          mutate(excl_count = str_count(reviewText, "!")) %>%
                          group_by(company_id) %>%
                          mutate(total_excl_count = sum(excl_count),
                                 exl_prop = total_excl_count/char_length)

model22 <- lm(log(avg_rating)~total_excl_count,data = syntactical_info_excl)
model23 <- lm(log(avg_rating)~exl_prop,data = syntactical_info_excl)

#Calculating the number of capital letter words in each store
syntactical_info_caps <-  dataset %>% left_join(company_id_avg_rating) %>% 
                          left_join(all_together_sentiments_company) %>%
                          mutate(cap_count = str_count(reviewText, "[[:upper:]]")) %>%
                          group_by(company_id) %>%
                          mutate(total_cap_count = sum(cap_count),
                                 cap_prop = total_cap_count/char_length)

model24 <- lm(log(avg_rating)~total_cap_count,data = syntactical_info_caps)
model25 <- lm(log(avg_rating)~cap_prop,data = syntactical_info_caps)

stargazer::stargazer(model22,model23,model24,model25,type = "text")

#Regressing exclamations with sentiment
model26 <- lm(bing_liu_sentiment~total_excl_count, data = syntactical_info_excl)
model27 <- lm(sentiment_nrc~total_excl_count, data = syntactical_info_excl)
model28 <- lm(sentiment_affin~total_excl_count, data = syntactical_info_excl)
model29 <- lm(sentiment_loughran~total_excl_count, data = syntactical_info_excl)

stargazer::stargazer(model26,model27,model28,model29,type = "text")

#Regressing capital letters with sentiment
model30 <- lm(bing_liu_sentiment~total_cap_count, data = syntactical_info_caps)
model31 <- lm(sentiment_nrc~total_cap_count, data = syntactical_info_caps)
model32 <- lm(sentiment_affin~total_cap_count, data = syntactical_info_caps)
model33 <- lm(sentiment_loughran~total_cap_count, data = syntactical_info_caps)

stargazer::stargazer(model30,model31,model32,model33,type = "text")
```


# Part C

In this section, we will perform topic modelling using the Latent Dirichlet allocation method.

We will initially perform an unsupervised topic modelling approach and then compare it with a supervised approach.

Upon analysis, we will try to identify the optimum kappa value for the number of topics to be selected. Using the kappa value, we will identify the topics using semantic coherence and exclusivity. 
Finally, we will try to associate the effects of the topics and metadata with the ratings. We will also try to sense the importance of topics over regions and years.

* Loading relevant libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(dplyr)
library(qdap)
library(stringr)
library(tidytext)
library(cld2)
library(tm)
library(textmineR)
library(textclean)
library(textstem)
library(wordcloud)
library(reshape2)
library(topicmodels)
library(lubridate)
#install.packages('stm')
library(stm)
```

* Loading the dataset from previous section

```{r}
#Importing the dataset
dataset <- readRDS("review_data_en.rds")
dataset_stores <- readRDS("review_data_by_stores.rds")
```

* Cleaning the reviews

We will now do some text cleaning that wil be necessary for this section

```{r}
#Checking the structure of the dataset
str(dataset)

#data cleaning
dataset$reviewText <- iconv(dataset$reviewText)
dataset$reviewText <- replace_non_ascii(dataset$reviewText) #replacing common non-ascii words
dataset$reviewText <- gsub("[ |\t]+", " ", dataset$reviewText) #removing white space
dataset$reviewText <- gsub("[^\x01-\x7F]", "", dataset$reviewText) #removing emoticons
dataset$reviewText <- gsub("<.*>", "", dataset$reviewText) #removing emojis
dataset$reviewText <- lemmatize_words(dataset$reviewText) #lemmatizing words
dataset$reviewText <- gsub("[ |\t]+", " ", dataset$reviewText) #removing white space
```

# LDA Topic modelling approach (Unsupervised)

Here, we will perform unsupervised topic modelling. We will try to identify the topics without taking the target variable into account. 

We are going to use the manual LDA method for this approach. However, the following method could also be used to do unsupervised modelling. We will use the supervised version of the similar code later.

{
**reviews_fit_11 <- stm(documents = out$documents,
                   vocab = out$vocab,
                   K = 0,
                   max.em.its = 75, 
                   data = out$meta,
                   sigma.prior = 0.5,
                   init.type = "Spectral") #to allow the function to find the optimum number of topics
}

## Finding topics for store level

For the unsupervised approach, we will group all the individual reviews into one company review to find the topics. This should allow us to explore the topics without any effect of review levels or ratings.

* Casting a dtm

```{r}
LDA_custom_words <- c("ve", "don", "service", "company", "customer", "business", "product")
tibble(word = LDA_custom_words,lexicon = rep("custom",length(LDA_custom_words))) %>% bind_rows(stop_words) -> LDA_custom_stopwords

topic_dtm <- dataset_stores %>%  
             unnest_tokens(word,grouped_reviews) %>% anti_join(LDA_custom_stopwords) %>% 
             count(company_id,word) %>% cast_dtm(company_id,word,n)
inspect(topic_dtm)

topic_dtm_sparse <- tm::removeSparseTerms(topic_dtm,sparse = 0.68)
inspect(topic_dtm_sparse)
```

* Creating an LDA model

We will initiate by choosing a random kappa value

```{r}
#Creating model with random kappa value for evaluation
topic_model <- LDA(topic_dtm, k = 2, method = "Gibbs")
topic_model_sparse <- LDA(topic_dtm_sparse, k = 2, method = "Gibbs")
```

* For kappa selection

Now that we have got a dummy model, we search for an optimum value to k by using perplexity values. We will aim for the lowest perplexity value excluding the terminal ends.

```{r}
set.seed(123)
#Setting a number range
topics <- c(2:20)

#Getting perplexity values
perplexity_df <- data.frame(perp_value=numeric())
for (i in topics){
  fitted <- LDA(topic_dtm, k = i, method = "Gibbs")
  perplexity_df[i,1] <- perplexity(topic_model,topic_dtm)
}

#Getting perplexity values
perplexity_df_sparse <- data.frame(perp_value=numeric())
for (i in topics){
  fitted <- LDA(topic_dtm_sparse, k = i, method = "Gibbs")
  perplexity_df[i,1] <- perplexity(topic_model_sparse,topic_dtm_sparse)
}

#Plotting the results
perplexity_plot <- ggplot(data=perplexity_df, 
       aes(x=as.numeric(row.names(perplexity_df)))) +
  labs(y="Perplexity",x="Number of topics", title="Perplexity") +
  geom_line(aes(y=perp_value), colour="black") +
  geom_point(aes(y=perp_value),size=2) +
  theme_bw() +
  theme(panel.grid.minor = element_blank())

perplexity_plot <- ggplot(data=perplexity_df_sparse, 
       aes(x=as.numeric(row.names(perplexity_df_sparse)))) +
  labs(y="Perplexity",x="Number of topics", title="Perplexity") +
  geom_line(aes(y=perp_value), colour="black") +
  geom_point(aes(y=perp_value),size=2) +
  theme_bw() +
  theme(panel.grid.minor = element_blank())

ggsave("perplexity.png")
```

From the graph, we see that perplexity is lowest at k = 12. We will now search for 12 topics.

* Topic modelling for k = 12 

```{r}
#Creating the model
topic_model_12 <- LDA(topic_dtm, k = 12, method = "Gibbs", control = list(seed = 1234))
topic_model_8_sparse <- LDA(topic_dtm_sparse, k = 8, method = "Gibbs", control = list(seed = 123))

#Tidying the output
lda_12_topics_beta <- tidy(topic_model_12, matrix = "beta")
lda_8_topics_beta_sparse <- tidy(topic_model_8_sparse, matrix = "beta")

#Getting the top terms for each topic
lda_12_beta_top_terms <- lda_12_topics_beta %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

lda_8_beta_top_terms_sparse <- lda_8_topics_beta_sparse %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

#Plotting the topic words
lda_12_beta_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()

lda_8_beta_top_terms_sparse %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```
Based on the plot, we will now understand the topic labels that can be used for the word sets.

```{r}
topic_labels <- c("phone_payment", "product_quality", "friendly_staff", "call_issues", "refunds", "item_delivery", "customer_support", "website_quality")
```


* Getting the document level values(gamma)
```{r}
#Tidying the model
gamma_topics <- tidy(topic_model_8_sparse,matrix="gamma")
gamma_topics <- gamma_topics %>% 
                pivot_wider(names_from = topic, values_from = gamma)

#Setting the column names
colnames(gamma_topics) <- c("document",topic_labels)

#Removing the document from the column
rownames(gamma_topics) <- gamma_topics$document
gamma_topics$document <- NULL 
```

* Plotting topic relations
```{r}
#Topic correlations
corrplot::corrplot(cor(gamma_topics))
```

```{r}
#Factor relation
pcah <- FactoMineR::PCA(gamma_topics,graph = FALSE)
factoextra::fviz_pca_var(pcah)
```

* Checking topics for bigrams
```{r}
topic_bi_dtm <- dataset_stores %>%  
                unnest_tokens(word,grouped_reviews, token = "ngrams", n = 2) %>% 
                separate(word, c("word1", "word2"), sep = " ") %>%
                filter(!word1 %in% LDA_custom_stopwords$word) %>%
                filter(!word2 %in% LDA_custom_stopwords$word) %>%
                unite("word", word1, word2, sep = " ") %>%
                count(company_id,word) %>% cast_dtm(company_id,word,n)
```

```{r}
#Creating the model
topic_model_bi <- LDA(topic_bi_dtm, k = 8, method = "Gibbs", control = list(seed = 1234))

#Tidying the output
lda_bi_topics_beta <- tidy(topic_model_bi, matrix = "beta")

#Getting the top terms for each topic
lda_bi_beta_top_terms <- lda_bi_topics_beta %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>% 
  ungroup() %>%
  arrange(topic, -beta)

#Plotting the topic words
lda_bi_beta_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```


# STM topic modelling approach

* POS Tagging
```{r}
#Downloading the model for the english language 
langmodel_download <- udpipe::udpipe_download_model("english")

#Loading the model 
langmodel <- udpipe::udpipe_load_model(langmodel_download$file_model)
```

* Annotating the reviews with POS
```{r}
#creating an empty dataframe
annotated_reviews_all <- data.frame()

#setting a split size for the data
split_size <- 1000

#splitting the dataset according to set split size
for_pos_list <- split(dataset, 
                     rep(1:ceiling(nrow(dataset)
                                   /split_size), 
                         each=split_size,
                         length.out=nrow(dataset)))

#annotating the parts of speech using the language model
for(i in 1:length(for_pos_list)){
    udpipe::udpipe_annotate(for_pos_list[[i]]$reviewText,
                doc_id = for_pos_list[[i]]$review_id,
                object = langmodel) %>% 
    as.data.frame() %>% 
    filter(upos %in% c("NOUN","ADJ","ADV")) %>%
    dplyr::select(doc_id,lemma) %>% 
    group_by(doc_id) %>% 
    summarise(annotated_reviews = paste(lemma, collapse = " ")) %>% 
    rename(review_id = doc_id) -> this_annotated_reviews
  
  print(paste(i,"from",length(for_pos_list)))
  annotated_reviews_all <- bind_rows(annotated_reviews_all,
                                     this_annotated_reviews)
}
```

* Prepping data for STM model
```{r}
#Setting the datatype of the review_id variable for use in stm model
annotated_reviews_all$review_id <- as.integer(annotated_reviews_all$review_id)

#combining the annotated reviews with the main dataset to be used for stm modelling
data_for_stm <- annotated_reviews_all %>% 
                left_join(dataset)  

#Setting the datatype of the reviewer ratings for use in stm model
data_for_stm$reviewer_rating <- as.integer(data_for_stm$reviewer_rating)
```

```{r}
#processing the data through automated cleaning of function
processed <- textProcessor(data_for_stm$annotated_reviews,
                           metadata = data_for_stm,
                           customstopwords = c("customer", "review", "ever", "even", "site", "business", "also",  "just", "still", "one", "able", "many"),
                           stem = F)

#keep those words who appear more than 1% in the document corpus
threshold <- round(1/100 * length(processed$documents),0)

#getting the final data to be used in stm model
out <- prepDocuments(processed$documents,
                     processed$vocab,
                     processed$meta,
                     lower.thresh = threshold)
```

* Evaluating the kappa value
```{r}
#searching for optimal k value
numtopics <- searchK(out$documents,out$vocab,K=seq(from=2, to=20,by=1))

#plotting the result
plot(numtopics)
```

```{r}
numtopics$results %>%
  dplyr::select(K, exclus, semcoh) %>%
  filter(K %in% c(1:20)) %>%
  unnest() %>%
  mutate(K = as.factor(K)) %>%
  ggplot(aes(semcoh, exclus, color = K)) +
  geom_point(size = 2, alpha = 0.7) +
  labs(x = "Semantic coherence",
       y = "Exclusivity",
       title = "Comparing exclusivity and semantic coherence",
       subtitle = "Models with fewer topics have higher semantic coherence for more topics, but lower exclusivity")
```

* STM for 11 topics
```{r}
# for 11 topics
reviews_fit_11 <- stm(documents = out$documents,
                   vocab = out$vocab,
                   prevalence = ~ reviewer_rating,
                   K = 11,
                   max.em.its = 75, 
                   data = out$meta,
                   sigma.prior = 0.5,
                   init.type = "LDA")

#see top words for each topic
summary(reviews_fit_11)

#visualise top words in wordcloud
set.seed(1)
stm::cloud(reviews_fit_11,topic = 1)
stm::cloud(reviews_fit_11,topic = 2)
stm::cloud(reviews_fit_11,topic = 3)
stm::cloud(reviews_fit_11,topic = 4)
stm::cloud(reviews_fit_11,topic = 5)
stm::cloud(reviews_fit_11,topic = 6)
stm::cloud(reviews_fit_11,topic = 7)
stm::cloud(reviews_fit_11,topic = 8)
stm::cloud(reviews_fit_11,topic = 9)
stm::cloud(reviews_fit_11,topic = 10)
stm::cloud(reviews_fit_11,topic = 11)

#visualize topics
plot(reviews_fit_11, type="summary")

#visualizing topic quality with respect to exclusivity and semantic coherence
topicQuality(reviews_fit_11,documents = out$documents)
```

* Visualizing the top words in each topic
```{r}
stm_11_topics_beta <- tidy(reviews_fit_11, matrix = "beta")

#Getting the top terms for each topic
stm_11_topics_beta <- stm_11_topics_beta %>%
                      group_by(topic) %>%
                      slice_max(beta, n = 10) %>% 
                      ungroup() %>%
                      arrange(topic, -beta)

#Plotting the topic words
stm_11_topics_beta %>% mutate(term = reorder_within(term, beta, topic)) %>%
                       ggplot(aes(beta, term, fill = factor(topic))) +
                       geom_col(show.legend = FALSE) +
                       facet_wrap(~ topic, scales = "free") +
                       scale_y_reordered()
```

* Finding labels for the topics
```{r}
#getting the model summary
topic_summary <- summary(reviews_fit_11)

#see top reviews for each topic
topic_proportions <- colMeans(reviews_fit_11$theta)

#assigning the topic names as column headers
topic_labels <- c("Transactional Issues", "Reliable delivery", "Waiting Time", "Product Satisfaction", "Service", "Phone Issues", "Work", "Team Behavior", "Webpage", "Delivery Process", "Repairs")

#assembling the topic words in table according to proportions
table_to_write_labels <- data.frame()
for(i in 1:length(topic_summary$topicnums)){

   row_here <- tibble(topicnum= topic_summary$topicnums[i],
                      topic_label = topic_labels[i],
                      proportion = 100*round(topic_proportions[i],3),
                     frex_words = paste(topic_summary$frex[i,1:7],
                                        collapse = ", "))
   table_to_write_labels <- rbind(row_here,table_to_write_labels)
}
(table_to_write_labels %>% arrange(topicnum))
```

* Finding the correlations and factors for the topics
```{r}
library(FactoMineR)

#extracting metadata and gamma values
gamma_topics <- cbind(out$meta, reviews_fit_11$theta)

#processing dataset to use for correlation
gamma_topics$doc_id <- 1:nrow(gamma_topics)
gamma_topics <- gamma_topics %>% dplyr::select(22:33)
rownames(gamma_topics) <- gamma_topics$doc_id
gamma_topics$doc_id <- NULL
colnames(gamma_topics) <- paste0("topic_", 1:11)

#checking topic correlations
topic.corr <- topicCorr(reviews_fit_11)
plot(topic.corr)
```
```{r}
#checking factor relations
pcah <- FactoMineR::PCA(gamma_topics, graph = FALSE)
factoextra::fviz_pca_var(pcah)
```
* Looking at the effects of metadata on the topics
```{r}
#Predicting topics by reviewer ratings
predict_topics_ratings <- estimateEffect(~ reviewer_rating, stmobj = reviews_fit_11, metadata = out$meta)

#Visualizing the effects of reviewer ratings
plot(predict_topics_ratings, covariate = "reviewer_rating", topics = c(1:11),
 model = reviews_fit_11, method = "difference",
 cov.value1 = "5", cov.value2 = "1",
 xlab = "Low Rating … High Rating",
 main = "",
 xlim = c(-0.08,0.08),
 custom.labels = topic_labels,
 labeltype = "custom")
```

```{r}
#Observing topic prevalence over time
predict_topics_years <- estimateEffect(~ year, stmobj = reviews_fit_11, metadata = out$meta)

#Visualizing the effects of reviewer ratings
for(i in 1:length(topic_labels)){
  
  i <-   (plot(predict_topics_years, covariate = "year",
          topics = i,
          model = review_fit_11, method = "continuous",
          xlab = "Year",
          main = topic_labels[i],
          printlegend = FALSE,
          custom.labels =topic_labels[i],
          labeltype = "custom"))
}
```
* Checking the prevalence of topics over time
```{r}
#Getting the theta values and years
stm_object <- reviews_fit_11$theta
colnames(stm_object) <- paste0("topic_",1:11)
year_topics <- cbind(out$meta, stm_object)

#Summarizing the theta values by years
year_topic_prevalence <- year_topics %>% group_by(year) %>% summarise(topic1=mean(topic_1),
            topic2 = mean(topic_2),
            topic3 = mean(topic_3),
            topic4 = mean(topic_4),
            topic5 = mean(topic_5),
            topic6 = mean(topic_6),
            topic7 = mean(topic_7),
            topic8 = mean(topic_8),
            topic9 = mean(topic_9),
            topic10 = mean(topic_10),
            topic11 = mean(topic_11))
year_topic_prevalence <- pivot_longer(year_topic_prevalence, 2:11, names_to = "topics", values_to = "theta")

#Visualizing the outcome
year_topic_prevalence %>% group_by(topics, year) %>% ggplot(aes(x = year, y = theta, color = topics)) + geom_point() + facet_wrap(~ topics) + labs(color = "Topics", x = "Years (2011-2022)", y = "Topic prevalence", title = "Prevalence of each topic over the years")
```

* Checking the prevalence of topics by top countries
```{r}
#Finding the top 5 countries with most reviews
top_countries <- dataset %>% group_by(country) %>% summarise(total_reviews = n()) %>% arrange(desc(total_reviews)) %>% top_n(5) %>% dplyr::select(country)

#Getting the theta values and countries
stm_object <- reviews_fit_11$theta
colnames(stm_object) <- paste0("topic_",1:11)
country_topics <- cbind(out$meta, stm_object)
country_topics <- top_countries %>% left_join(country_topics)

#Summarizing the theta values by top 5 countries
country_topic_prevalence <- country_topics %>% group_by(country) %>% summarise(topic1=mean(topic_1),
            topic2 = mean(topic_2),
            topic3 = mean(topic_3),
            topic4 = mean(topic_4),
            topic5 = mean(topic_5),
            topic6 = mean(topic_6),
            topic7 = mean(topic_7),
            topic8 = mean(topic_8),
            topic9 = mean(topic_9),
            topic10 = mean(topic_10),
            topic11 = mean(topic_11))
country_topic_prevalence <- pivot_longer(country_topic_prevalence, 2:12, names_to = "topics", values_to = "theta")

#Visualizing the outcome
country_topic_prevalence %>% group_by(topics, country) %>% ggplot(aes(x = topics, y = theta, color = country)) + geom_point() + facet_wrap(~ topics) + labs(color = "Country", x = "Countries (Canada, France, Great Britain, Ireland, United States)", y = "Topic prevalence", title = "Prevalence of each topics in top 5 countries")
```

```{r}
stm_object <- reviews_fit_11$theta
colnames(stm_object) <- paste0("topic_",1:11)
final_regression <- cbind(stm_object, out$meta)

country_topic_prevalence <- country_topics %>% group_by(country) %>% summarise(topic1=mean(topic_1),
            topic2 = mean(topic_2),
            topic3 = mean(topic_3),
            topic4 = mean(topic_4),
            topic5 = mean(topic_5),
            topic6 = mean(topic_6),
            topic7 = mean(topic_7),
            topic8 = mean(topic_8),
            topic9 = mean(topic_9),
            topic10 = mean(topic_10),
            topic11 = mean(topic_11))
country_topic_prevalence <- pivot_longer(country_topic_prevalence, 2:12, names_to = "topics", values_to = "theta")
```

```{r}
# regression testing
TrainingData_with_variables_over_sentimentr_afinn_tf <-  
  readRDS("TrainingData_with_variables_over_sentimentr_afinn_tf.rds")

#combining with sentiments
train.data.theta <- TrainingData_with_variables_over_sentimentr_afinn_tf %>%
  left_join(theta_summary, by = c("review_id", "overall"))  %>%
  na.omit()

#removing variables not used in regression model
train.data.theta <- train.data.theta %>% dplyr::select(!c(review_id, reviewFull, 
                                                          lose_protection))  

#creating the base and topic information for regression
train.data.theta.base <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic3, mtopic4, mtopic5, mtopic6, mtopic7))
train.data.theta.base.topic1 <- train.data.theta %>% dplyr::select(
  !c(mtopic2, mtopic3, mtopic4, mtopic5, mtopic6, mtopic7))
train.data.theta.base.topic2 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic3, mtopic4, mtopic5, mtopic6, mtopic7))
train.data.theta.base.topic3 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic4, mtopic5, mtopic6, mtopic7))
train.data.theta.base.topic4 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic3, mtopic5, mtopic6, mtopic7))
train.data.theta.base.topic5 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic3, mtopic4, mtopic6, mtopic7))
train.data.theta.base.topic6 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic3, mtopic4, mtopic5, mtopic7))
train.data.theta.base.topic7 <- train.data.theta %>% dplyr::select(
  !c(mtopic1, mtopic2, mtopic3, mtopic4, mtopic5, mtopic6))

#creating regression models for all topics
model_base <-polr(overall~., train.data.theta.base,Hess = TRUE)
model_1 <- polr(overall~., train.data.theta.base.topic1,Hess = TRUE)
model_2 <-polr(overall~., train.data.theta.base.topic2,Hess = TRUE)
model_3 <-polr(overall~., train.data.theta.base.topic3,Hess = TRUE)
model_4 <-polr(overall~., train.data.theta.base.topic4,Hess = TRUE)
model_5 <-polr(overall~., train.data.theta.base.topic5,Hess = TRUE)
model_6 <-polr(overall~.,  train.data.theta.base.topic6,Hess = TRUE)
model_7 <-polr(overall~., topic_7,Hess = TRUE)
```
